### 2017-04-18 draft1.tex
adding small changes and latex doc

\documentclass{article}

\usepackage{listings}
\usepackage{color} %red, green, blue, yellow, cyan, magenta, black, white
\definecolor{mygreen}{RGB}{28,172,0} % color values Red, Green, Blue
\definecolor{mylilas}{RGB}{170,55,241}

\title{Sections and Chapters}
\author{Gubert Farnsworth}
\date{ ENME 625: Multi-Displinary Optimization \\ 5/12/2017}

\begin{document}

\maketitle

\newpage

\tableofcontents

\newpage

\section{Introduction}

This is the first section.

Lorem  ipsum  dolor  sit  amet,  consectetuer  adipiscing  
elit.   Etiam  lobortisfacilisis sem.  Nullam nec mi et 
neque pharetra sollicitudin.  Praesent imperdietmi nec ante. 
Donec ullamcorper, felis non sodales...

\addcontentsline{toc}{section}{Unnumbered Section}
\section*{Unnumbered Section}

Lorem ipsum dolor sit amet, consectetuer adipiscing elit.  
Etiam lobortis facilisissem.  Nullam nec mi et neque pharetra 
sollicitudin.  Praesent imperdiet mi necante...

\section{Constrained MOGA Problems}

Lorem ipsum dolor sit amet, consectetuer adipiscing elit.  
Etiam lobortis facilisissem.  Nullam nec mi et neque pharetra 
sollicitudin.  Praesent imperdiet mi necante...

\lstset{language=Matlab,%
    %basicstyle=\color{red},
    breaklines=true,%
    morekeywords={matlab2tikz},
    keywordstyle=\color{blue},%
    morekeywords=[2]{1}, keywordstyle=[2]{\color{black}},
    identifierstyle=\color{black},%
    stringstyle=\color{mylilas},
    commentstyle=\color{mygreen},%
    showstringspaces=false,%without this there will be a symbol in the places where there is a space
    numbers=left,%
    numberstyle={\tiny \color{black}},% size of the numbers
    numbersep=8pt, % this defines how far the numbers are from the text
    emph=[1]{for,end,break},emphstyle=[1]\color{red}, %some words to emphasise
    %emph=[2]{word1,word2}, emphstyle=[2]{style},    
}

\section*{Matlab Code}

\lstinputlisting{MasterCode.m}
\lstinputlisting{fitFCN5.m}

\end{document}

### 2017-04-18 MasterCode.m

@@ -1,7 +1,7 @@
-function MasterCode(prob,nChrome,nRun,save_figure);
+function MasterCode(prob,nChrome,nRun,save_figure)
 %clear all; 
 % close all;
-clc;
+%clc;
 warning off
 
 if(nargin < 1)
@@ -72,8 +72,11 @@ end
 
 Pareto = [];
 options = optimoptions(@ga,'PopulationSize',nChrome,'UseVectorized',true);
+%options.FunctionTolerance = 0.001*options.FunctionTolerance
+
 optF =[];
 for gen = 1:nRun
+    %Obj_fcn = @(X) fitFCN8(X,problem_function,optF);
     Obj_fcn = @(X) fitFCN5(X,problem_function);
     [X,fval,exitflag,output] = ga(Obj_fcn,nvar,A,b,Aeq,beq,LB,UB,[],options);
     [optF(gen,:)] = problem_function(X);

### 2017-04-18 fitFCN8.m

@@ -1,0 +1,242 @@
+function [ fit ] = fitFCN8(X, ZD_func,existing_points)
+%NSGA algorithm. Use Approach 1 for sorting
+
+func = ZD_func(X);
+
+% 
+% if isempty(existing_points)
+%     fit = sum(ZD_func(X));
+%     return 
+% end
+
+%% Find Dominate Points
+
+% Modify existing code to find Pareto points to find dominant layers
+
+% func = [existing_points;ZD_func(X)];
+nfunc = func(1,end-2);
+nconstr = func(1,end-1);
+g = func(:,nfunc+1:nfunc+nconstr);
+nconstr_lin = func(1,end);
+h = func(:,nfunc+nconstr+1:nfunc+nconstr+nconstr_lin);
+func = func(:,1:nfunc);
+
+[M,~] = size(X);
+
+
+
+
+if nconstr == 0 && nconstr_lin ==0
+    nc_col = nfunc + 3;
+    init_fit_col = nfunc + 4;
+    sim_col = nfunc+5;
+    indecies = [1:M]';
+    func = [func,indecies]; %We need to know indecies later so this should save time
+    P_temp = func;
+    level = 0;
+    level_col = nfunc +2;
+    func(:,level_col) = 0;
+    while ~isempty(P_temp)
+        level = level+1;% increment the level value
+        if length(P_temp(:,1))== 1
+            %If there is only one value left at the end, assign this to a level
+            func(P_temp(:,nfunc+1),level_col) = level;
+            break 
+        end
+        place = paretoset(P_temp(:,1:nfunc)); % get all the indecies in the lowest layer
+        for k = 1:length(place)
+            if place(k) == 1
+                current_level_indecies = P_temp(k,nfunc+1); %map them from
+                func(current_level_indecies, level_col) = level; % assiged from prtp
+            end
+        end     
+
+        P_temp(place, :) = [];
+    end
+
+    numLayer = level; 
+
+    %Make sure all individuals have a layer number
+    flag = 0;
+    for k = 1:M
+       if func(level_col)==0
+           func(k,level_col) = numLayer+1;
+           flag = 1;
+       end
+    end
+    if flag == 1, numLayer = numLayer+1; end
+
+    %% Similarity
+    %Assess similarity layer-by-layer, assess in objective space.
+
+    sigma = 0.75;
+    epsilon = 0.25;
+    alpha = 1;
+    var_rem = 0;
+    F_min = M+epsilon;
+    for k = 1:numLayer
[…]

### 2017-04-20 MasterCode.m
Add files via upload

@@ -1,30 +1,29 @@
-function MasterCode(prob,nChrome,nRun,save_figure)
-%clear all; 
+clear all; 
 % close all;
-%clc;
+clc;
 warning off
 
-if(nargin < 1)
-    prompt = 'Which Test Problem Do You Want To Run? \n 1 - ZDT1\n 2 - ZDT2 \n 3 - ZDT3 \n 4 - OSY \n';
-    prob = input(prompt);
-end
-if nargin <2
-    prompt2 = 'How Many Chromosomes? Suggest 20-30 ';
-    nChrome = input(prompt2);
-end
-if nargin <3
-    prompt3 = 'How Many Runs? Suggest >40: ';
-    nRun = input(prompt3);
-end
-if nargin <4
-    prompt4 = 'Autosave figures [ 1 or 0 ]?';
-    save_figure=input(prompt4);
-end
+global alpha sigma epsilon
 
+prompt = 'Which Test Problem Do You Want To Run? \n 1 - ZDT1\n 2 - ZDT2 \n 3 - ZDT3 \n 4 - OSY \n';
+prob = input(prompt);
+prompt2 = 'How Many Chromosomes? Suggest 10-20 times #variables: ';
+nChrome = input(prompt2);
+prompt3 = 'How Many Runs? Suggest >40: ';
+nRun = input(prompt3);
+prompt4 = 'What value for alpha? ';
+alpha = input(prompt4);
+prompt5 = 'What value for sigma? (Nominal 0.158) ';
+sigma = input(prompt5);
+prompt6 = 'What value for epsilon? (Nominal 0.22) ';
+epsilon = input(prompt6);
 %%
 %prob=1; nChrome = 1; nRun = 40;
 
-
+% for prob = 2:4
+%     clearvars -except prob;
+%     nChrome = 30;
+%     nRun = 2000;
 
 % ZD-func is our problem function
 switch prob
@@ -40,12 +39,6 @@ switch prob
     case 4
         problem_function = @(X) OSY(X);
         nvar = 6; LB = [0,0,1,0,1,0]; UB = [10,10,5,6,5,10];
-    case 5 
-        problem_function = @(X) TNK(X);
-        nvar = 2; LB = [0,0]; UB=[pi,pi];
-    case 6
-        problem_function = @(X) CTP(X);
[…]

### 2017-04-20 fitFCN5.m

@@ -1,6 +1,7 @@
 function [ fit ] = fitFCN5(X, ZD_func)
 %NSGA algorithm. Use Approach 1 for sorting
 
+global alpha sigma epsilon
 func = ZD_func(X);
 
 % 
@@ -69,9 +70,9 @@ if nconstr == 0 && nconstr_lin ==0
     %% Similarity
     %Assess similarity layer-by-layer, assess in objective space.
 
-    sigma = 0.75;
-    epsilon = 0.25;
-    alpha = 1;
+    sigma = 0.158;
+    epsilon = 0.1;
+%     alpha = 1;
     var_rem = 0;
     F_min = M+epsilon;
     for k = 1:numLayer
@@ -125,8 +126,6 @@ if nconstr == 0 && nconstr_lin ==0
 %% Constraint Handling
 else
     Cmax = 1.2; Cmin = 0.8; r = 0.8*M; 
-    %CF1 = 0.0005+(0.015-0.0005)*rand;
-    %CF2 = 0.0005+(0.015-0.0005)*rand;
     CF1 = 0.01;
     CF2 = 0.01;
     rank = zeros(1,M);

### 2017-04-20 draft1.tex
updating tex file

@@
 \documentclass{article}
-
+\usepackage{graphicx}
+\graphicspath{{figures/}}
+\usepackage{subfigure}
 \usepackage{listings}
@@
 
-Lorem  ipsum  dolor  sit  amet,  consectetuer  adipiscing  
-elit.   Etiam  lobortisfacilisis sem.  Nullam nec mi et 
-neque pharetra sollicitudin.  Praesent imperdietmi nec ante. 
-Donec ullamcorper, felis non sodales...
+\addcontentsline{toc}{section}{Problems}
+\section*{Unconstrained MOGA Problems}
+We used this textbook \cite{deb2001multi}
 
-\addcontentsline{toc}{section}{Unnumbered Section}
-\section*{Unnumbered Section}
-
-Lorem ipsum dolor sit amet, consectetuer adipiscing elit.  
-Etiam lobortis facilisissem.  Nullam nec mi et neque pharetra 
-sollicitudin.  Praesent imperdiet mi necante...
+\subsection{ ZDT1} 
+Talk about ZDT1 here.
 
 \section{Constrained MOGA Problems}
+This is a reference to Azarms constraint paper \cite{kurpati2002constraint}. %This is how references are read from the references.bib file.
 
-Lorem ipsum dolor sit amet, consectetuer adipiscing elit.  
-Etiam lobortis facilisissem.  Nullam nec mi et neque pharetra 
-sollicitudin.  Praesent imperdiet mi necante...
+\subsection{TNK}
+
+Here is figure \ref{fig:TNK}.
+
+\begin{figure}%[tbp]
+  \centering
+  \includegraphics[width=0.50\columnwidth]{5_020_1000.png}
+  \caption{ This is TNK for 20 chromosomes and 1000 runs}
+  \label{fig:TNK}
+\end{figure}
+
+\vspace{-0.1in}
+\bibliographystyle{IEEEtran}
+\bibliography{references.bib}
+
+\section{Appendix}
+
+%Matlab codes starts here
 

### 2017-04-20 MasterCode.m
Add files via upload

@@ -1,30 +1,29 @@
-function MasterCode(prob,nChrome,nRun,save_figure)
-%clear all; 
+clear all; 
 % close all;
-%clc;
+clc;
 warning off
 
-if(nargin < 1)
-    prompt = 'Which Test Problem Do You Want To Run? \n 1 - ZDT1\n 2 - ZDT2 \n 3 - ZDT3 \n 4 - OSY \n';
-    prob = input(prompt);
-end
-if nargin <2
-    prompt2 = 'How Many Chromosomes? Suggest 20-30 ';
-    nChrome = input(prompt2);
-end
-if nargin <3
-    prompt3 = 'How Many Runs? Suggest >40: ';
-    nRun = input(prompt3);
-end
-if nargin <4
-    prompt4 = 'Autosave figures [ 1 or 0 ]?';
-    save_figure=input(prompt4);
-end
+global alpha sigma epsilon
 
+prompt = 'Which Test Problem Do You Want To Run? \n 1 - ZDT1\n 2 - ZDT2 \n 3 - ZDT3 \n 4 - OSY \n';
+prob = input(prompt);
+prompt2 = 'How Many Chromosomes? Suggest 10-20 times #variables: ';
+nChrome = input(prompt2);
+prompt3 = 'How Many Runs? Suggest >40: ';
+nRun = input(prompt3);
+prompt4 = 'What value for alpha? ';
+alpha = input(prompt4);
+prompt5 = 'What value for sigma? (Nominal 0.158) ';
+sigma = input(prompt5);
+prompt6 = 'What value for epsilon? (Nominal 0.22) ';
+epsilon = input(prompt6);
 %%
 %prob=1; nChrome = 1; nRun = 40;
 
-
+% for prob = 2:4
+%     clearvars -except prob;
+%     nChrome = 30;
+%     nRun = 2000;
 
 % ZD-func is our problem function
 switch prob
@@ -40,12 +39,6 @@ switch prob
     case 4
         problem_function = @(X) OSY(X);
         nvar = 6; LB = [0,0,1,0,1,0]; UB = [10,10,5,6,5,10];
-    case 5 
-        problem_function = @(X) TNK(X);
-        nvar = 2; LB = [0,0]; UB=[pi,pi];
-    case 6
-        problem_function = @(X) CTP(X);
[…]

### 2017-04-20 fitFCN5.m

@@ -1,6 +1,7 @@
 function [ fit ] = fitFCN5(X, ZD_func)
 %NSGA algorithm. Use Approach 1 for sorting
 
+global alpha sigma epsilon
 func = ZD_func(X);
 
 % 
@@ -69,9 +70,9 @@ if nconstr == 0 && nconstr_lin ==0
     %% Similarity
     %Assess similarity layer-by-layer, assess in objective space.
 
-    sigma = 0.75;
-    epsilon = 0.25;
-    alpha = 1;
+%     sigma = 0.158;
+%     epsilon = 0.1;
+%     alpha = 1;
     var_rem = 0;
     F_min = M+epsilon;
     for k = 1:numLayer
@@ -125,8 +126,6 @@ if nconstr == 0 && nconstr_lin ==0
 %% Constraint Handling
 else
     Cmax = 1.2; Cmin = 0.8; r = 0.8*M; 
-    %CF1 = 0.0005+(0.015-0.0005)*rand;
-    %CF2 = 0.0005+(0.015-0.0005)*rand;
     CF1 = 0.01;
     CF2 = 0.01;
     rank = zeros(1,M);

### 2017-04-20 MasterCode.m
before merge

@@ -1,11 +1,16 @@
-function MasterCode(prob,nChrome,nRun,save_figure)
+function [optF]=MasterCode(prob,nChrome,nRun,save_figure,use_matlabs_moga)
+% load .mat file
+current_dir = pwd;
+file_name = [current_dir, current_dir(1),'results_and_params.mat'];
+results_and_params = load(file_name);
+
 %clear all; 
 % close all;
 %clc;
 warning off
 
 if(nargin < 1)
-    prompt = 'Which Test Problem Do You Want To Run? \n 1 - ZDT1\n 2 - ZDT2 \n 3 - ZDT3 \n 4 - OSY \n';
+    prompt = 'Which Test Problem Do You Want To Run? \n 1 - ZDT1\n 2 - ZDT2 \n 3 - ZDT3 \n 4 - OSY \n 5 - TNK \n 6 - CTP \n';
     prob = input(prompt);
 end
 if nargin <2
@@ -20,55 +25,64 @@ if nargin <4
     prompt4 = 'Autosave figures [ 1 or 0 ]?';
     save_figure=input(prompt4);
 end
+if nargin <5
+    prompt5 = 'Use Matlabs MOGA [ 1 or 0 ]?';
+    use_matlabs_moga=input(prompt5);
+end
 
-%%
-%prob=1; nChrome = 1; nRun = 40;
-
-
+problem = results_and_params(prob,1);
 
 % ZD-func is our problem function
 switch prob
     case 1
         problem_function = @(X) ZDT1(X);
         nvar = 30; LB = zeros(1,nvar); UB = ones(1,nvar);
+        problem_contraints = [];
     case 2 
         problem_function = @(X) ZDT2(X);
         nvar = 30; LB = zeros(1,nvar); UB = ones(1,nvar);
+        problem_contraints = [];
     case 3
         problem_function = @(X) ZDT3(X);
         nvar = 30; LB = zeros(1,nvar); UB = ones(1,nvar);
+        problem_contraints = [];
     case 4
         problem_function = @(X) OSY(X);
         nvar = 6; LB = [0,0,1,0,1,0]; UB = [10,10,5,6,5,10];
+        problem_contraints  =@(X) OSY_constraints(X);
     case 5 
         problem_function = @(X) TNK(X);
         nvar = 2; LB = [0,0]; UB=[pi,pi];
+        problem_contraints  =@(X) TNK_constraints(X);
     case 6
         problem_function = @(X) CTP(X);
[…]

### 2017-04-21 MasterCode.m
Add files via upload
Updated MasterCode to include TNK_Robust. 
Updated fitFCN5 to include robustness fitness evaluation (around lines 150)
Updated functions to include variable which indicates whether to run robustness measures or not
Added TNK_Robust and negative version of TNK constraints (for delta_P maximization)

@@ -1,9 +1,9 @@
 function [optX,optF]=MasterCode(prob,nChrome,nRun,alpha_,sigma_,epsilon_,save_figure,use_matlabs_moga)
 % load .mat file
-current_dir = pwd;
-file_name = [current_dir, current_dir(1),'results_and_params.mat'];
-results_and_params = load(file_name);
-results_and_params = results_and_params.results_and_params;
+% current_dir = pwd;
+% file_name = [current_dir, current_dir(1),'results_and_params.mat'];
+% results_and_params = load(file_name);
+% results_and_params = results_and_params.results_and_params;
 global alpha sigma epsilon
 
 if(nargin < 1)
@@ -45,7 +45,7 @@ if nargin <8
     use_matlabs_moga=input(prompt8);
 end
 
-problem = results_and_params{prob,1};
+% problem = results_and_params{prob,1};
 
 % ZD-func is our problem function
 switch prob
@@ -74,7 +74,10 @@ switch prob
         problem_function = @(X) CTP(X);
         nvar = 10; LB = -5*ones(1,10); UB = 5*ones(1,10); LB(1,1) = 0; UB(1,1) = 1;
         problem_constraints = @CTP_constraints; % Only used in matlab test
-
+    case 7 
+        DP=1;
+        problem_function = @(X) TNK_Robust(X,DP);
+        nvar = 2; LB = [0,0]; UB=[pi,pi]; 
     otherwise 
         problem_function = @(X) 0;
 end

### 2017-04-21 TNK_Robust.m

@@ -1,15 +1,16 @@
-function [f,constraint] = TNK(X)
+%For incorporation into exisiting code
+function [f,constraint] = TNK_Robust(X,DP)
 
 f1 = X(:,1);
 f2 = X(:,2);
-g1 = -(X(:,1).^2 +X(:,2).^2 -1 -0.1*cos(16*atan2(X(:,1),X(:,2))));
+g1 = -(X(:,1).^2 +X(:,2).^2 -1 -0.1*cos(16*atan2(X(:,1),X(:,2)))-0.2*sin(DP)*cos(DP));
 g2 = (X(:,1)-0.5).^2 + (X(:,2)-0.5).^2 -0.5;
 constraint = [g1 g2];
 
 nfunc = 2*ones(length(X(:,1)),1);
 nconstr = 2*ones(length(X(:,1)),1);
 nconstr_lin = 0*ones(length(X(:,1)),1);
-UNCT = 0*ones(length(X(:,1)),1);
+UNCT = 1*ones(length(X(:,1)),1);
 
 f = [f1,f2,constraint,nfunc,nconstr,nconstr_lin,UNCT];
 

### 2017-04-21 ZDT1.m

@@ -10,8 +10,9 @@ F2 = g.*h;
 nfunc = 2*ones(length(X(:,1)),1);
 nconstr = 0*ones(length(X(:,1)),1);
 nconstr_lin = 0*ones(length(X(:,1)),1);
+UNCT = 0*ones(length(X(:,1)),1);
 
-f = [F1,F2,nfunc,nconstr,nconstr_lin];
+f = [F1,F2,nfunc,nconstr,nconstr_lin,UNCT];
 
 end
 

### 2017-04-21 ZDT3.m

@@ -11,8 +11,9 @@ F2 = g.*h;
 nfunc = 2*ones(length(X(:,1)),1);
 nconstr = 0*ones(length(X(:,1)),1);
 nconstr_lin = 0*ones(length(X(:,1)),1);
+UNCT = 0*ones(length(X(:,1)),1);
 
-f = [F1,F2,nfunc,nconstr,nconstr_lin];
+f = [F1,F2,nfunc,nconstr,nconstr_lin,UNCT];
 
 
 

### 2017-04-21 MasterCode.m
trying to deal with windows

@@ -1,7 +1,8 @@
 function [optX,optF]=MasterCode(prob,nChrome,nRun,alpha_,sigma_,epsilon_,save_figure,use_matlabs_moga)
 % load .mat file
 current_dir = pwd;
-file_name = [current_dir, current_dir(1),'results_and_params.mat'];
+file_name = 'results_and_params.mat';
+%file_name = [current_dir, current_dir(1),'results_and_params.mat'];
 results_and_params = load(file_name);
 results_and_params = results_and_params.results_and_params;
 global alpha sigma epsilon

### 2017-04-21 MasterCode.m
worked on robust part

@@ -133,8 +133,13 @@ end
 
 % figure
 hold on;
-ml_optF = problem.matlab_optF;
-plot(ml_optF(:,1),ml_optF(:,2),'b*')
+if isempty(problem)==false
+    if(isfield(problem,'matlab_optF'))
+        ml_optF = problem.matlab_optF;
+        plot(ml_optF(:,1),ml_optF(:,2),'b*')
+    end
+end
+
 if(isempty(Pareto) == false)
     plot(Pareto(:,1),Pareto(:,2),'gv','LineWidth',2,'MarkerSize',10)
 end

### 2017-04-21 TNK_NEGCN2.m

@@ -1,6 +1,6 @@
 %Fitness function for innerloop GA, used to evaluate fitness of MOGA
 %results. Updated to be negative INSIDE the function.
-function [eta_gnew] = TNK_NEGCN(X,DP)
+function [eta_gnew] = TNK_NEGCN2(X,DP)
 % assuming that p_0 will not change
 g1   = 1+0.1.*cos(16.*atan2(X(1),X(2)))+0.2.*sin(1+DP(:,1)).*cos(1+DP(:,2))+X(1)^2 +X(2)^2;
 g1_o = 1+0.1.*cos(16.*atan2(X(1),X(2)))+0.2.*sin(1).*cos(1)+X(1)^2 +X(2)^2;

### 2017-04-21 fitFCN5.m

@@ -156,8 +156,8 @@ else
              if rank(k) == 0.5*M
                  options = optimoptions(@ga,'PopulationSize',10,'UseVectorized',true);
                  lb = -2; ub = 2;
-                 fitnessfn = @(DP) TNK_NEGCN(XOLin(k,:),DP);
-                 [DP,fval] = ga(fitnessfn,1,[],[],[],[],lb,ub,[],options);
+                 fitnessfn = @(DP) -TNK_NEGCN2(XOLin(k,:),DP);
+                 [DP,fval] = ga(fitnessfn,2,[],[],[],[],lb,ub,[],options);
                  Constval = fval;
                  if Constval > 0
                      rank(k) = 0;

### 2017-04-22 MasterCode.m
things seem to be working

@@ -87,8 +87,9 @@ switch prob
         problem_constraints = @CTP_constraints; % Only used in matlab test
     case 7 
         DP=1;
-        problem_function = @(X) TNK_Robust(X,DP);
-        nvar = 2; LB = [0,0]; UB=[pi,pi]; 
+        problem_function = @(X,DP) TNK_Robust(X,DP);
+        nvar = 2; LB = [0,0]; UB=[pi,pi];
+        robust_fitness = @(X,DP) TNK_NEGCN2(X,DP);
     otherwise 
         problem_function = @(X) 0;
 end
@@ -117,11 +118,16 @@ options = optimoptions(@ga,'PopulationSize',nChrome,'UseVectorized',true,'Crosso
 optF =[];
 for gen = 1:nRun
     Obj_fcn = @(X) fitFCN5(X,problem_function);
-    [X,fval,~,~] = ga(Obj_fcn,nvar,A,b,Aeq,beq,LB,UB,[],options);
-    [optF(gen,:)] = problem_function(X);
+    if(prob==7);Obj_fcn = @(X) fitFCN5(X,problem_function,robust_fitness);end
+    [X,~,~,~] = ga(Obj_fcn,nvar,A,b,Aeq,beq,LB,UB,[],options);
+    if(prob==7)
+        [optF(gen,:)] = problem_function(X,[0,0]);
+    else
+        [optF(gen,:)] = problem_function(X);
+    end
     optX(gen,:) = X;
 end
-nfunc = optF(1,end-2);
+nfunc = 2; % Making this static because it will not change in this project
 
 P = paretoset(optF(:,1:nfunc));
 m = 1;
@@ -143,7 +149,7 @@ end
 if(isempty(Pareto) == false)
     plot(Pareto(:,1),Pareto(:,2),'gv','LineWidth',2,'MarkerSize',10)
 end
-% plot(optF(:,1),optF(:,2),'r*','LineWidth',2)
+ plot(optF(:,1),optF(:,2),'r*','LineWidth',2)
 hold on; grid on;
 xlabel('f_1'); ylabel('f_2')
 

### 2017-04-22 TNK_NEGCN2.m

@@ -1,16 +1,17 @@
 %Fitness function for innerloop GA, used to evaluate fitness of MOGA
 %results. Updated to be negative INSIDE the function.
 function [eta_gnew] = TNK_NEGCN2(X,DP)
+
+%Using page 4 of MORO.pdf
 % assuming that p_0 will not change
-g1   = 1+0.1.*cos(16.*atan2(X(1),X(2)))+0.2.*sin(1+DP(:,1)).*cos(1+DP(:,2))+X(1)^2 +X(2)^2;
-g1_o = 1+0.1.*cos(16.*atan2(X(1),X(2)))+0.2.*sin(1).*cos(1)+X(1)^2 +X(2)^2;
+g1   = 1+0.1.*cos(16.*atan2(X(1),X(2)))+0.2.*sin(1+DP(:,1)).*cos(1+DP(:,2))-X(1)^2 -X(2)^2;
+g1_o = 1+0.1.*cos(16.*atan2(X(1),X(2)))+0.2.*sin(1).*cos(1)-X(1)^2 -X(2)^2;
 
 g2   = (X(1)-0.5).^2 + (X(2)-0.5).^2 -0.5;
 g2_o = (X(1)-0.5).^2 + (X(2)-0.5).^2 -0.5;
 
-
+%get delta g_j 
 [rows,~] = size(DP);
-
 delta_g1 = zeros(rows,1);
 val = (g1 -g1_o)/abs(g1_o);
 delta_g1(g1 >= g1_o) = val(g1 >= g1_o);
@@ -19,7 +20,7 @@ delta_g2 = zeros(rows,1);
 val = (g2 -g2_o)/abs(g2_o);
 delta_g2(g2 >= g2_o) = val;
 
-
+%return eta_gnew
 eta_gnew = sqrt(sum([delta_g1,delta_g2].^2,2));
 end
 

### 2017-04-22 TNK_Robust.m

@@ -1,9 +1,10 @@
 %For incorporation into exisiting code
 function [f,constraint] = TNK_Robust(X,DP)
 
+
 f1 = X(:,1);
 f2 = X(:,2);
-g1 = -(X(:,1).^2 +X(:,2).^2 -1 -0.1*cos(16*atan2(X(:,1),X(:,2)))-0.2*sin(DP)*cos(DP));
+g1 = 1  +0.1*cos(16*atan2(X(:,1),X(:,2)))+0.2*sin(DP(:,1)+1).*cos(DP(:,2)+1) - X(:,1).^2 -X(:,2).^2;
 g2 = (X(:,1)-0.5).^2 + (X(:,2)-0.5).^2 -0.5;
 constraint = [g1 g2];
 

### 2017-04-22 fitFCN5.m

@@ -1,8 +1,37 @@
-function [ fit ] = fitFCN5(X, ZD_func)
+function [ fit ] = fitFCN5(X, ZD_func,robust_constraint_fitness)
 %NSGA algorithm. Use Approach 1 for sorting
-
 global alpha sigma epsilon
-func = ZD_func(X);
+
+cheat = 1;
+
+if nargin < 3
+    robust_constraint_fitness = [];
+end
+
+%Check is this is a robust problem
+delta_P = [];
+if isempty(robust_constraint_fitness)
+    func = ZD_func(X);
+else%Evaluates feasible solutions with uncertaintly applied in problems with
+%uncertainy
+    if cheat ==1
+        delta_P = [0.5708*ones(length(X),1),-1*ones(length(X),1)];
+    else
+        [M,~] = size(X);
+        for k = 1:M
+            options = optimoptions(@ga,'PopulationSize',10,'UseVectorized',true);
+            lb = [-2,-2]; ub = [2,2];
+            fitnessfn = @(DP) -TNK_NEGCN2(X(k,:),DP);
+            [d_p,~] = ga(fitnessfn,2,[],[],[],[],lb,ub,[],options);
+            delta_P = [delta_P ; d_p];
+        end
+    end
+    func = ZD_func(X,delta_P);
+end
+
+
+
+
 
 % 
 % if isempty(existing_points)
@@ -16,12 +45,13 @@ func = ZD_func(X);
 
 % func = [existing_points;ZD_func(X)];
 
-XOLin = X;
-UNCT = func(1,end);
 nfunc = func(1,end-3);
 nconstr = func(1,end-2);
 g = func(:,nfunc+1:nfunc+nconstr);
 nconstr_lin = func(1,end-1);
+if nconstr_lin > 0
+    fprintf('weird error here')
+end
 h = func(:,nfunc+nconstr+1:nfunc+nconstr+nconstr_lin);
 func = func(:,1:nfunc);
 
@@ -149,26 +179,7 @@ else
         end
      end
     
-     %Evaluates feasible solutions with uncertaintly applied in problems with
-    %uncertainy
-     if UNCT == 1
-         for k = 1:M
-             if rank(k) == 0.5*M
-                 options = optimoptions(@ga,'PopulationSize',10,'UseVectorized',true);
-                 lb = -2; ub = 2;
-                 fitnessfn = @(DP) -TNK_NEGCN2(XOLin(k,:),DP);
[…]

### 2017-04-22 MasterCode.m
MasterCode no longer a function

@@ -1,6 +1,6 @@
-function [optX,optF]=MasterCode(prob,nChrome,nRun,alpha_,sigma_,epsilon_,save_figure,use_matlabs_moga)
+%function [optX,optF]=MasterCode(prob,nChrome,nRun,alpha_,sigma_,epsilon_,save_figure,use_matlabs_moga)
 % load .mat file
-
+nargin=0;
 current_dir = pwd;
 %file_name = 'results_and_params.mat';
 if(contains(current_dir,'/ENME625_Optimization')) %linux or mac
@@ -18,7 +18,7 @@ results_and_params = results_and_params.results_and_params;
 global alpha sigma epsilon
 
 if(nargin < 1)
-    prompt = 'Which Test Problem Do You Want To Run? \n 1 - ZDT1\n 2 - ZDT2 \n 3 - ZDT3 \n 4 - OSY \n 5 - TNK \n 6 - CTP \n';
+    prompt = 'Which Test Problem Do You Want To Run? \n 1 - ZDT1\n 2 - ZDT2 \n 3 - ZDT3 \n 4 - OSY \n 5 - TNK \n 6 - CTP \n 7 - Robust TNK \n';
     prob = input(prompt);
 end
 if nargin <2

### 2017-04-23 FlightPathOpt.m
adding last problem

@@ -1,0 +1,117 @@
+% This script demonstrates the use of the optimization toolbox to solve a
+% simple pathfinding problem. We are given an airplane with a fixed
+% airspeed and a vector field of wind in which to navigate. The objective
+% is to find the path which minimizes the time taken to travel from the
+% starting point to the finish point.
+%
+% Copyright (c) 2012, MathWorks, Inc. 
+%
+
+%% First make some random vector field of wind, and set parameters
+
+clear; clf;
+
+AirSpeed = 500;
+sizeX = 50;
+sizeY = 25;
+numWayPoints = 5;
+rng(50);
+
+W_x = makeWindFun(sizeX,sizeY);
+W_y = makeWindFun(sizeX,sizeY);
+
+[Xgrid,Ygrid] = meshgrid(0:sizeX,0:sizeY);
+hq = quiver(Xgrid,Ygrid,W_x,W_y,'k');
+hold on;
+xlabel('Units = 100 [km]');
+axis equal tight
+plot([0 sizeX],[sizeY sizeY]/2,'k.','markersize',16)
+
+%% Add some color to make it more visible
+L = (sqrt((Xgrid-sizeX).^2 + (Ygrid-sizeY/2).^2));
+Favorability = ((sizeX-Xgrid).*W_x +  (sizeY/2-Ygrid).*W_y)./L; 
+Favorability(~isfinite(Favorability)) = 0; 
+
+hold on;
+h_im = imagesc(Favorability); % This will be the background for the vector field
+
+set(h_im,'Xdata',[0 sizeX],'Ydata',[0 sizeY]);
+uistack(h_im,'bottom');
+
+% Change the colormap...
+colormap(interp1([0,1,2],[1 0 0; 1 1 1; 0 1 0],0:0.01:2));
+caxis(max(abs(Favorability(:)))*[-1 1]);
+
+h_colorbar = colorbar;
+title(h_colorbar,'Tailwind (km/h)')
+xlabel(h_colorbar,'Headwind')
+
+%% Generate a default set of way points
+xWayPoints = linspace(0,sizeX,numWayPoints+2)';
+yWayPoints = sizeY/2 * ones(numWayPoints+2,1);
+
+h_wp = plot(xWayPoints,yWayPoints,'color','k','linestyle','none','marker','.','markersize',16);
+
+%% Generate a continuous path from the waypoints
[…]

### 2017-04-23 FlightPathOpt.m
works with ml moga

@@ -74,22 +74,25 @@ delete([h_wp h_path]);
 h_wp = plot(xWayPoints,yWayPoints,'color','k','linestyle','none','marker','.','markersize',16);
 
 % Generate a continuous path from the waypoints
-PathPoints = WayPoints_To_Path([xWayPoints,yWayPoints],'cubic',sizeX,sizeY,101);
+PathPoints = WayPoints_To_Path([xWayPoints,yWayPoints],'PCHIP',sizeX,sizeY,101);
 h_path = plot(PathPoints(:,1),PathPoints(:,2),'k','linewidth',2);
 
 LineTime = getTimeFromPath(PathPoints,W_x,W_y,AirSpeed);
 fprintf('Travel Time: %d hours, %.1f minutes\n',floor(LineTime),rem(LineTime,1)*60);
+%% Add No Fly Zone
+xc = 40; yc = 20; radius = 10;
+for i = 1:length(xc)
+    t = linspace(0,2*pi);
+    x_bounds = xc(i)+radius(i)*cos(t);
+    x_bounds(x_bounds >sizeX) = sizeX;
+    x_bounds(x_bounds < 0) =0;
+    y_bounds = yc(i)+radius(i)*sin(t);
+    y_bounds(y_bounds >sizeY) = sizeY;
+    y_bounds(y_bounds < 0) = 0;
+    plot(x_bounds,y_bounds);
+end
 
-%% Find an optimal path using FMINCON
-% Define Objective Function
-objectiveFun = @(P) getTimeFromPath(P,W_x,W_y,AirSpeed,sizeX,sizeY,'PCHIP');
-
-% Set optimization options
-opts = optimset('fmincon');
-opts.Display = 'iter';
-opts.Algorithm = 'active-set';
-opts.MaxFunEvals = 2000;
-
+%% Optimization
 % Initial Conditions
 xWayPoints = linspace(0,sizeX,numWayPoints+2)';
 yWayPoints = sizeY/2 * ones(numWayPoints+2,1);
@@ -100,8 +103,46 @@ ic = ic(:);
 lb = zeros(size(ic(:)));
 ub = reshape([sizeX*ones(1,numWayPoints); sizeY*ones(1,numWayPoints)],[],1);
 
-%Do the optimizaiton
-optimalWayPoints = fmincon(objectiveFun, ic(:), [],[],[],[],lb,ub,[],opts)
+% Define 1st Objective Function
[…]

### 2017-04-23 FlightPathOpt.m
Now with working distance maximization

@@ -80,7 +80,7 @@ h_path = plot(PathPoints(:,1),PathPoints(:,2),'k','linewidth',2);
 LineTime = getTimeFromPath(PathPoints,W_x,W_y,AirSpeed);
 fprintf('Travel Time: %d hours, %.1f minutes\n',floor(LineTime),rem(LineTime,1)*60);
 %% Add No Fly Zone
-xc = 40; yc = 20; radius = 10;
+xc = [40,20]; yc = [5,20]; radius = [5,5];
 for i = 1:length(xc)
     t = linspace(0,2*pi);
     x_bounds = xc(i)+radius(i)*cos(t);
@@ -122,9 +122,9 @@ if(single_objective == 1)
     optimalWayPoints = fmincon(objectiveFun, ic(:), [],[],[],[],lb,ub,[],opts);
 else
     %% Find an optimal path using GAMultiobh
+    population_size = 20;
     %Define 2nd Objective Function
-    %distanceFromExclusionZone =@(P) -max(sum((P(:,1) - xc(1)).^2 +(P(:,2) -yc(1)).^2,10) );
-    distanceFromExclusionZone =@(P) 1;
+    distanceFromExclusionZone =@(P) -0.1*getDistanceExclustionZone(P,sizeX,sizeY,xc,yc,radius);
     
     %Define bi-objective Function
     problem_function= @(P) [objectiveFun(P) distanceFromExclusionZone(P)];
@@ -135,24 +135,29 @@ else
     problem_constraints = []; % Removing problem constraints for now
     %Do the optimization using multiobjective optimizations
     options = optimoptions('gamultiobj');
-    options = optimoptions(options,'PopulationSize',100);
+    options = optimoptions(options,'PopulationSize',population_size);
     options = optimoptions(options,'CrossoverFcn', @crossoverscattered);
     options = optimoptions(options,'Display', 'final');
     %options = optimoptions(options,'PlotFcn', { @gaplotpareto });
     options = optimoptions(options,'ParetoFraction', 0.9);
     [X,FVAL,EXITFLAG,OUTPUT,POPULATION,SCORE] = gamultiobj(problem_function,length(ic),[],[],[],[],lb,ub,problem_constraints,options);
-    optimalWayPoints = X;
 end
 
 %% Plot the optimal solution:
[…]

### 2017-04-23 getDistanceExclustionZone.m

@@ -1,0 +1,19 @@
+function closest_dist = getDistanceExclustionZone(P,sizeX,sizeY,xc,yc,radius)
+% Tell you how close you will get to the exclusion zone with a path.  
+
+METHOD = 'PCHIP';
+
+%Convert waypooints to path
+if isvector(P)
+    PathPoints = [0 sizeY/2; reshape(P,2,[])'; sizeX sizeY/2];
+    PathPoints = WayPoints_To_Path(PathPoints,METHOD,sizeX,sizeY,101);
+end
+
+squared_dist = zeros(length(radius),1);
+
+for i = 1:length(radius)
+    squared_dist(i) = min((PathPoints(:,1) - xc(i)).^2 +(PathPoints(:,2) -yc(i)).^2 );
+end
+
+
+closest_dist = sqrt(min(squared_dist));

### 2017-04-23 FlightPathOpt.m
Fixed some plotting bugs

@@ -19,7 +19,7 @@ rng(50);
 
 W_x = makeWindFun(sizeX,sizeY);
 W_y = makeWindFun(sizeX,sizeY);
-
+figure(1)
 [Xgrid,Ygrid] = meshgrid(0:sizeX,0:sizeY);
 hq = quiver(Xgrid,Ygrid,W_x,W_y,'k');
 hold on;
@@ -124,14 +124,14 @@ else
     %% Find an optimal path using GAMultiobh
     population_size = 20;
     %Define 2nd Objective Function
-    distanceFromExclusionZone =@(P) -0.1*getDistanceExclustionZone(P,sizeX,sizeY,xc,yc,radius);
+    distanceFromExclusionZone =@(P) -0.1*min(getDistanceExclustionZone(P,sizeX,sizeY,xc,yc,radius));
     
     %Define bi-objective Function
     problem_function= @(P) [objectiveFun(P) distanceFromExclusionZone(P)];
 
     %Define Constraint Function
-    ineq_constraints = @(P) -sum((P(:,1) - xc(1)).^2 +(P(:,2) -yc(1)).^2 -radius(1));
-    problem_constraints = @(P) deal(ineq_constraints(P),0);
+    ineq_constraints = @(P) radius(:) -getDistanceExclustionZone(P,sizeX,sizeY,xc,yc,radius) ;
+    problem_constraints = @(P) [ ineq_constraints(P),0];
     problem_constraints = []; % Removing problem constraints for now
     %Do the optimization using multiobjective optimizations
     options = optimoptions('gamultiobj');
@@ -157,7 +157,7 @@ for i= i:population_size
 end
 LineTime = getTimeFromPath(PathPoints,W_x,W_y,AirSpeed);
 fprintf('Optimal Travel Time: %d hours, %.1f minutes\n',floor(LineTime),rem(LineTime,1)*60);
-
+figure(2)
 plot(FVAL(:,1),10*FVAL(:,2),'g^')
 xlabel('Flight Time')
 ylabel('Closest Point to Exclusion Zone')

### 2017-04-23 getDistanceExclustionZone.m

@@ -1,4 +1,4 @@
-function closest_dist = getDistanceExclustionZone(P,sizeX,sizeY,xc,yc,radius)
+function dist = getDistanceExclustionZone(P,sizeX,sizeY,xc,yc,radius)
 % Tell you how close you will get to the exclusion zone with a path.  
 
 METHOD = 'PCHIP';
@@ -9,11 +9,11 @@ if isvector(P)
     PathPoints = WayPoints_To_Path(PathPoints,METHOD,sizeX,sizeY,101);
 end
 
-squared_dist = zeros(length(radius),1);
+dist = zeros(length(radius),1);
 
 for i = 1:length(radius)
-    squared_dist(i) = min((PathPoints(:,1) - xc(i)).^2 +(PathPoints(:,2) -yc(i)).^2 );
+    dist(i) = sqrt(min((PathPoints(:,1) - xc(i)).^2 +(PathPoints(:,2) -yc(i)).^2 ));
 end
 
 
-closest_dist = sqrt(min(squared_dist));
+%closest_dist = sqrt(min(squared_dist));

### 2017-04-23 FlightPathOpt.m
Now with non-robust constraints

@@ -19,6 +19,7 @@ rng(50);
 
 W_x = makeWindFun(sizeX,sizeY);
 W_y = makeWindFun(sizeX,sizeY);
+clf(figure(1))
 figure(1)
 [Xgrid,Ygrid] = meshgrid(0:sizeX,0:sizeY);
 hq = quiver(Xgrid,Ygrid,W_x,W_y,'k');
@@ -80,7 +81,7 @@ h_path = plot(PathPoints(:,1),PathPoints(:,2),'k','linewidth',2);
 LineTime = getTimeFromPath(PathPoints,W_x,W_y,AirSpeed);
 fprintf('Travel Time: %d hours, %.1f minutes\n',floor(LineTime),rem(LineTime,1)*60);
 %% Add No Fly Zone
-xc = [40,20]; yc = [5,20]; radius = [5,5];
+xc = [5,40,20]; yc = [5,5,20]; radius = [5,10,10];  %Alter these params to get different no-fly zones
 for i = 1:length(xc)
     t = linspace(0,2*pi);
     x_bounds = xc(i)+radius(i)*cos(t);
@@ -130,9 +131,9 @@ else
     problem_function= @(P) [objectiveFun(P) distanceFromExclusionZone(P)];
 
     %Define Constraint Function
-    ineq_constraints = @(P) radius(:) -getDistanceExclustionZone(P,sizeX,sizeY,xc,yc,radius) ;
-    problem_constraints = @(P) [ ineq_constraints(P),0];
-    problem_constraints = []; % Removing problem constraints for now
+    problem_constraints = @(P) flightConstraints(P,sizeX,sizeY,xc,yc,radius); 
+    %problem_constraints = []; % Removing problem constraints for now
+    
     %Do the optimization using multiobjective optimizations
     options = optimoptions('gamultiobj');
     options = optimoptions(options,'PopulationSize',population_size);

### 2017-04-23 getDistanceExclustionZone.m

@@ -1,11 +1,12 @@
-function dist = getDistanceExclustionZone(P,sizeX,sizeY,xc,yc,radius)
-% Tell you how close you will get to the exclusion zone with a path.  
+function dist = getDistanceExclustionZone(PathPoints,sizeX,sizeY,xc,yc,radius)
+% Tell you how close you will get to the exclusion zones with a path.  
+% returns a value for each exclusion zone
 
 METHOD = 'PCHIP';
 
 %Convert waypooints to path
-if isvector(P)
-    PathPoints = [0 sizeY/2; reshape(P,2,[])'; sizeX sizeY/2];
+if isvector(PathPoints)
+    PathPoints = [0 sizeY/2; reshape(PathPoints,2,[])'; sizeX sizeY/2];
     PathPoints = WayPoints_To_Path(PathPoints,METHOD,sizeX,sizeY,101);
 end
 
@@ -15,5 +16,5 @@ for i = 1:length(radius)
     dist(i) = sqrt(min((PathPoints(:,1) - xc(i)).^2 +(PathPoints(:,2) -yc(i)).^2 ));
 end
 
-
+constraints = radius' - dist;
 %closest_dist = sqrt(min(squared_dist));

### 2017-04-23 draft1_SM.tex
Add files via upload

\documentclass{article}
\usepackage{graphicx}
\graphicspath{{figures/}}
\usepackage{subfigure}
\usepackage{amsmath}
\usepackage{listings}

\usepackage{color} %red, green, blue, yellow, cyan, magenta, black, white
\definecolor{mygreen}{RGB}{28,172,0} % color values Red, Green, Blue
\definecolor{mylilas}{RGB}{170,55,241}

\title{Sections and Chapters}
\author{Gubert Farnsworth}
\date{ ENME 625: Multi-Displinary Optimization \\ 5/12/2017}

\begin{document}

\maketitle

\newpage

\tableofcontents

\newpage

\section{Introduction}

This is the first section.

\addcontentsline{toc}{section}{Problems}
\section*{Unconstrained MOGA Problems}
We used this textbook \cite{deb2001multi}

\subsection{ZDT1} 
The first test problem, denoted as ZDT1 in (insert reference) is shown below.

\begin{align*}
\textrm{Minimize} ~~~~~ f_1(\textbf{x}) &= x_1 \\
\textrm{Minimize} ~~~~~ f_2(\textbf{x}) &= g(x)*h(x) \\
\textrm{where} ~~~~~~~~~~ g(x) &= 1+\frac{9}{(n-1)}\sum_{i=2}^{n}x_i \\
~~~~~~~~~~ h(x) &= 1- \sqrt{\frac{f_1(x)}{g(x)}} \\
~~~~~~~~~~ n &= 30 \\
0 &\leq  \textbf{x}  \leq 1 \\
\end{align*}

The true Pareto frontier for this problem occurs when $x_i = 0$ for i = 2,...,30. Figure~\ref{fig:ZDT1} shows a sample result from both MATLABs built in MOGA and the MOGA developed in this project. The quality metrics chosen to evaluate this problem are Coverage Difference (CD)and Pareto Spread (OS). Ten runs for each algorithm were performed and the mean and standard deviation of each metric are tabulated in Table~\ref{tab:ZDT1}.
\begin{figure}[h]
  \caption{Example Pareto Results for ZDT1}
  \centering
  \includegraphics[width=0.85\textwidth]{ZDT1_pareto_final.png}  
  \label{fig:ZDT1}
\end{figure}

\begin{table}[h]
\caption{Quality Metrics for ZDT1} 
\centering 
\begin{tabular}{|c|c|c|} 
\hline\hline  
Metric & MATLABs MOGA & Our MOGA \\ \hline
CD & 0.3874 (0.0164) &  0.3582 (0.0040) \\ \hline
OS & 0.9605 (0.1088) & 0.9283 (0.0928) \\ \hline
\end{tabular}
\label{tab:ZDT1} 
\end{table}
From these metrics, there is certainly a trade-off between MATLABs MOGA and the MOGA developed in this project. The coverage difference of the new MOGA is better in this problem whereas the Pareto spread is improved when using MATLABs MOGA.

\subsection{ZDT2} 
The second test problem, denoted as ZDT2 in (insert reference) is shown below.

\begin{align*}
\textrm{Minimize} ~~~~~ f_1(\textbf{x}) &= x_1 \\
\textrm{Minimize} ~~~~~ f_2(\textbf{x}) &= g(x)*h(x) \\
\textrm{where} ~~~~~~~~~~ g(x) &= 1+\frac{9}{(n-1)}\sum_{i=2}^{n}x_i \\
~~~~~~~~~~ h(x) &= 1- \frac{f_1(x)}{g(x)}^2 \\
~~~~~~~~~~ n &= 30 \\
0 &\leq  \textbf{x}  \leq 1 \\
\end{align*}

The true Pareto frontier for this problem, similar to ZDT1, occurs when $x_i$ = 0 for i = 2,...,30. Figure~\ref{fig:ZDT2} shows a sample result from both MATLABs built in MOGA and the MOGA developed in this project. Table~\ref{tab:ZDT2} summarizes the mean quality metrics for each algorithm for ten runs.
\begin{figure}[h!]
  \caption{Example Pareto Results for ZDT2}
  \centering
  \includegraphics[width=0.85\textwidth]{ZDT2_pareto_final.png}  
  \label{fig:ZDT2}
\end{figure}

\begin{table}[h]
\caption{Quality Metrics for ZDT2} 
\centering 
\begin{tabular}{|c|c|c|} 
\hline\hline  
Metric & MATLABs MOGA & Our MOGA \\ \hline
CD &  &   \\ \hline
OS &  &  \\ \hline
\end{tabular}
\label{tab:ZDT2} 
\end{table}

\subsection{ZDT3} 
The third test problem, denoted as ZDT3 in (insert reference) is shown below.

\begin{align*}
\textrm{Minimize} ~~~~~ f_1(\textbf{x}) &= x_1 \\
\textrm{Minimize} ~~~~~ f_2(\textbf{x}) &= g(x)*h(x) \\
\textrm{where} ~~~~~~~~~~ g(x) &= 1+\frac{9}{(n-1)}\sum_{i=2}^{n}x_i \\
~~~~~~~~~~ h(x) &= 1- \sqrt{\frac{f_1(x)}{g(x)}}- \frac{f_1(x)}{g(x)}\sin(10\pi f_1) \\
~~~~~~~~~~ n &= 30 \\
0 &\leq  \textbf{x}  \leq 1 \\
\end{align*}

The true Pareto frontier for this problem again occurs when $x_i$ = 0 for i = 2,...,30. Figure~\ref{fig:ZDT3} shows a sample result from both MATLABs built in MOGA and the MOGA developed in this project. Table~\ref{tab:ZDT3} summarizes the mean quality metrics for each algorithm for ten runs.
%\begin{figure}[h]
%  \caption{Example Pareto Results for ZDT3}
%  \centering
%  \includegraphics[width=0.85\textwidth]{ZDT3_pareto_final.png}  
%  \label{fig:ZDT3}
%\end{figure}

\begin{table}[h]
\caption{Quality Metrics for ZDT3} 
\centering 
\begin{tabular}{|c|c|c|} 
\hline\hline  
Metric & MATLABs MOGA & Our MOGA \\ \hline
CD &  &   \\ \hline
OS &  &  \\ \hline
\end{tabular}
\label{tab:ZDT3} 
\end{table}

\subsection{OSY} 
This test problem, denoted as OSY in (insert reference) is shown below.

\begin{align*}
\textrm{Minimize} ~~~~~ f_1(\textbf{x}) &= -(25(x_1-2)^2+(x_2-2)^2+(x_3-1)^2+(x_4-4)^2+(x_5-1)^2) \\
\textrm{Minimize} ~~~~~ f_2(\textbf{x}) &= \sum_{i=1}^{6}x_i^2 \\
\textrm{Subject to} ~~~~ g_1(x) &= 1-\frac{x_1+x_2}{2} \leq 0 \\
g_2(x) &= \frac{x_1+x_2}{6}-1 \leq 0 \\
g_3(x) &= \frac{x_2-x_1}{2}-1 \leq 0 \\
g_4(x) &= \frac{x_1-3x_2}{2}-1 \leq 0 \\
g_5(x) &= \frac{(x_3-3)^2+x_4}{4}-1 \leq 0 \\
g_6(x) &= 1-\frac{(x_5-3)^2+x_6}{4} \leq 0 \\
0 &\leq  x_1,x_2,x_6  \leq 10 \\
1 &\leq  x_3,x_5  \leq 5 \\
0 &\leq  x_4  \leq 6 \\
\end{align*}

The true Pareto frontier for this problem again occurs when $x_i$ = 0 for i = 2,...,30. Figure~\ref{fig:OSY} shows a sample result from both MATLABs built in MOGA and the MOGA developed in this project. Table~\ref{tab:OSY} summarizes the mean quality metrics for each algorithm for ten runs.
%\begin{figure}[h]
%  \caption{Example Pareto Results for OSY}
%  \centering
%  \includegraphics[width=0.85\textwidth]{OSY_pareto_final.png}  
%  \label{fig:OSY}
%\end{figure}

\begin{table}[h]
\caption{Quality Metrics for OSY} 
\centering 
\begin{tabular}{|c|c|c|} 
\hline\hline  
Metric & MATLABs MOGA & Our MOGA \\ \hline
CD &  &   \\ \hline
OS &  &  \\ \hline
\end{tabular}
\label{tab:OSY} 
\end{table}

\section{Constrained MOGA Problems}
This is a reference to Azarms constraint paper \cite{kurpati2002constraint}. %This is how references are read from the references.bib file.

\subsection{TNK} 
This test problem, denoted as TNK in (insert reference) is shown below.

\begin{align*}
\textrm{Minimize} ~~~~~ f_1(\textbf{x}) &= x_1 \\
\textrm{Minimize} ~~~~~ f_2(\textbf{x}) &= x_2 \\
\textrm{Subject to} ~~~~ g_1(x) &= -x_1^2-x_2^2+1+0.1\cos(16\arctan(\frac{x_1}{x_2})) \leq 0 \\
g_2(x) &= (x_1 - 0.5)^2 + (x_2 - 0.5)^2 -0.5 \leq 0 \\
0 &\leq  x_1,x_2 \leq \pi \\
\end{align*}

Figure~\ref{fig:TNK} shows a sample result from both MATLABs built in MOGA and the MOGA developed in this project. Table~\ref{tab:TNK} summarizes the mean quality metrics for each algorithm for ten runs.
%\begin{figure}[h]
%  \caption{Example Pareto Results for TNK}
%  \centering
%  \includegraphics[width=0.85\textwidth]{TNK_pareto_final.png}  
%  \label{fig:TNK}
%\end{figure}

\begin{table}[h]
\caption{Quality Metrics for TNK} 
\centering 
\begin{tabular}{|c|c|c|} 
\hline\hline  
Metric & MATLABs MOGA & Our MOGA \\ \hline
CD &  &   \\ \hline
OS &  &  \\ \hline
\end{tabular}
\label{tab:TNK} 
\end{table}

\subsection{CTP} 
This test problem, denoted as CTP in (insert reference) is shown below.

\begin{align*}
\textrm{Minimize} ~~~~~ f_1(\textbf{x}) &= x_1 \\
\textrm{Minimize} ~~~~~ f_2(\textbf{x}) &= g(x)(1-\sqrt{\frac{f_1(x)}{g(x)}} \\
\textrm{Subject to} ~~~~ g_1(x) &= a|\sin(b\pi(\sin(\theta)(f_2(x)-e)+\cos(\theta)f_1(x))^c)|^d \\
&- \cos(\theta)(f_2(x)-e)-\sin(\theta)f_1(x) \leq 0 \\
\textrm{where} ~~~~~~~~~~ \theta &= -0.2\pi, a = 0.2, b=10, c=1, d=6, e = 1 \\
g(x) &= |1+(\sum_{i=2}^{10}x_i)^{0.25}| \\
0 &\leq  x_1  \leq 1 \\
-5 &\leq  x_i  \leq 5, i = 2,...,10 \\
\end{align*}

Figure~\ref{fig:CTP} shows a sample result from both MATLABs built in MOGA and the MOGA developed in this project. Table~\ref{tab:CTP} summarizes the mean quality metrics for each algorithm for ten runs.
%\begin{figure}[h]
%  \caption{Example Pareto Results for CTP}
%  \centering
%  \includegraphics[width=0.85\textwidth]{CTP_pareto_final.png}  
%  \label{fig:CTP}
%\end{figure}

\begin{table}[h]
\caption{Quality Metrics for CTP} 
\centering 
\begin{tabular}{|c|c|c|} 
\hline\hline  
Metric & MATLABs MOGA & Our MOGA \\ \hline
CD &  &   \\ \hline
OS &  &  \\ \hline
\end{tabular}
\label{tab:CTP} 
\end{table}

\vspace{-0.1in}
\bibliographystyle{IEEEtran}
\bibliography{references.bib}

\section{Appendix}

%Matlab codes starts here

\lstset{language=Matlab,%
    %basicstyle=\color{red},
    breaklines=true,%
    morekeywords={matlab2tikz},
    keywordstyle=\color{blue},%
    morekeywords=[2]{1}, keywordstyle=[2]{\color{black}},
    identifierstyle=\color{black},%
    stringstyle=\color{mylilas},
    commentstyle=\color{mygreen},%
    showstringspaces=false,%without this there will be a symbol in the places where there is a space
    numbers=left,%
    numberstyle={\tiny \color{black}},% size of the numbers
    numbersep=8pt, % this defines how far the numbers are from the text
    emph=[1]{for,end,break},emphstyle=[1]\color{red}, %some words to emphasise
    %emph=[2]{word1,word2}, emphstyle=[2]{style},    
}

\section*{Matlab Code}

\lstinputlisting{MasterCode.m}
\lstinputlisting{fitFCN5.m}

\end{document}

### 2017-04-24 draft1_SM.tex
Update draft1_SM.tex

@@
 
-\addcontentsline{toc}{section}{Problems}
-\section*{Unconstrained MOGA Problems}
+\section{Unconstrained MOGA Problems}
 We used this textbook \cite{deb2001multi}
@@
 Metric & MATLABs MOGA & Our MOGA \\ \hline
-CD &  &   \\ \hline
-OS &  &  \\ \hline
+CD & 0.7832  (0.0821) & 0.6971  (0.0094) \\ \hline
+OS &  0.8781 (0.0946) & 1.0086 (0.0278)  \\ \hline
 \end{tabular}
@@
 Table~\ref{tab:ZDT3} summarizes the mean quality metrics for each algorithm for ten runs.
-%\begin{figure}[h]
-%  \caption{Example Pareto Results for ZDT3}
-%  \centering
-%  \includegraphics[width=0.85\textwidth]{ZDT3_pareto_final.png}  
-%  \label{fig:ZDT3}
-%\end{figure}
+
+\begin{figure}[h]
+  \caption{Example Pareto Results for ZDT3}
+  \centering
+  \includegraphics[width=0.85\textwidth]{ZDT3_pareto_final.png}  
+  \label{fig:ZDT3}
+\end{figure}
 
@@
 Metric & MATLABs MOGA & Our MOGA \\ \hline
-CD &  &   \\ \hline
-OS &  &  \\ \hline
+CD & 0.7407 (0.0050) & 0.7554 (0.0031) \\ \hline
+OS & 0.8565 (0.0098) & 0.8489 (0.0180) \\ \hline
 \end{tabular}
@@
 \end{table}
+
+Overall, MATLABs MOGA outperforms the MOGA developed in this project in both coverage difference and Pareto spread.
+A paired t-test shows that the difference in the means for coverage difference is statistically significant (p<0.05), while the difference is not statistically significant in Pareto Spread (p=0.21).
 
@@
 \subsection{TNK} 
-This test problem, denoted as TNK in (insert reference) is shown below.
+This test problem, denoted as TNK in (insert reference) is shown below with the true Pareto frontier shown in Figure~\ref{fig:TNK_true}.
 
@@
 \end{align*}
+\begin{figure}[h]
+  \caption{True Pareto Frontier for TNK}
+  \centering
+  \includegraphics[width=0.85\textwidth]{TNK_pareto_true.png}  
+  \label{fig:TNK_true}
+\end{figure}
 
@@
 Table~\ref{tab:TNK} summarizes the mean quality metrics for each algorithm for ten runs.
-%\begin{figure}[h]
-%  \caption{Example Pareto Results for TNK}
-%  \centering
-%  \includegraphics[width=0.85\textwidth]{TNK_pareto_final.png}  
-%  \label{fig:TNK}
-%\end{figure}
+\begin{figure}[h]
+  \caption{Example Pareto Results for TNK}
+  \centering
+  \includegraphics[width=0.85\textwidth]{TNK_pareto_final.png}  
+  \label{fig:TNK}
+\end{figure}
 
@@
 Metric & MATLABs MOGA & Our MOGA \\ \hline
-CD &  &   \\ \hline
-OS &  &  \\ \hline
+CD &  0.8581 (0.0480) & 0.7792 (0.0036) \\ \hline
+OS & 0.4177 (0.3216) & 0.9763 (0.0178)\\ \hline
 \end{tabular}
@@
 
+Comparing the estimated Pareto frontiers to the true Pareto frontier, is is clear that our MOGA outperforms MATLAB's MOGA.
+The Pareto spread in our MOGA is significantly higher however the coverage difference is higher in MATLABs MOGA (p<0.05).
+
 \subsection{CTP} 
-This test problem, denoted as CTP in (insert reference) is shown below.
+This test problem, denoted as CTP in (insert reference) is shown below and the true Pareto frontier is shown in Figure~\ref{fig:CTP_true}.
 
@@
 \end{align*}
+\begin{figure}[h]
+  \caption{True Pareto Frontier for CTP}
+  \centering
+  \includegraphics[width=0.85\textwidth]{CTP_pareto_true.png}  
+  \label{fig:CTP_true}
+\end{figure}
 
@@
 Table~\ref{tab:CTP} summarizes the mean quality metrics for each algorithm for ten runs.
-%\begin{figure}[h]
-%  \caption{Example Pareto Results for CTP}
-%  \centering
-%  \includegraphics[width=0.85\textwidth]{CTP_pareto_final.png}  
-%  \label{fig:CTP}
-%\end{figure}
+\begin{figure}[h]
+  \caption{Example Pareto Results for CTP}
+  \centering
+  \includegraphics[width=0.85\textwidth]{CTP_pareto_final.png}  
+  \label{fig:CTP}
+\end{figure}
 
@@
 Metric & MATLABs MOGA & Our MOGA \\ \hline
-CD &  &   \\ \hline
-OS &  &  \\ \hline
+CD & 0.6802 (0.0067) &  0.6802 (0.0092) \\ \hline
+OS & 0.7901 (0.0734) & 0.5959 (0.1324) \\ \hline
 \end{tabular}
@@
 
+The mean values for coverage difference are exactly the same for both algorithms.
+In fact a paired t-test also shows the means are not statistically difference(p>0.05).
+For Pareto spread, MATLAB's MOGA performs the highest.
+
+ \newpage
 \vspace{-0.1in}

### 2017-04-24 draft1_SM.tex
added last problem

@@
 Figure~\ref{fig:CTP} shows a sample result from both MATLABs built in MOGA and the MOGA developed in this project.
-Table~\ref{tab:CTP} summarizes the mean quality metrics for each algorithm for ten runs.
+Table~\ref{tab:CTP} summarizes the mean quality metrics for each algorithm for ten runs \cite{deb2001multi}.
 \begin{figure}[h]
@@
 For Pareto spread, MATLAB's MOGA performs the highest.
+
+\section{Flight Planning Problem (FPP)}
+Now let us consider the final problem where we try to minimize the total flight time from the start location $(0,12.5)$ to the finish location $(40,12.5)$.
+In this problem there is a know wind velocity field which changes the total velocity of the aircraft with respect to the ground.
+At the same time, we want to maximize the distance of the flight path from some group of some exclusion zones.
+This also introduces a constraint that requires the flight path not intersect the exclusion zone.
+Each exclusion zone is approximated by a circle with known centers.
+The radius of each exclusion zone is known to $\pm 2m$.
+As a result this problem can be approached as a bi-objective optimization with a robust feasibility constraint.
+
+\begin{align*}
+\textrm{Minimize} ~~~~~ f_1(\textbf{x},\textbf{y}) &= flightTime(\textbf{x},\textbf{y})\\
+\textrm{Maximize} ~~~~~ f_2(\textbf{x},\textbf{y}) &= -\min_{i,j}\sqrt{(\textbf{x}_i-\textbf{xc}_j)^2 + (\textbf{y}_i-\textbf{yc}_j)^2}\\
+\textrm{Subject to} ~~~~ \textbf{g}_j(\textbf{x},\textbf{y}) &= -\min_{j}\left[\textbf{r}_j+p_0 + \Delta p -\sqrt{(\textbf{x}_i-\textbf{xc}_j)^2 + (\textbf{y}_i-\textbf{yc}_j)^2}\right]   \leq 0 \\
+\textrm{where} ~~~~~~~~~~ 
+0 &\leq  x \leq 50, i = 2,...,10 \\
+0 &\leq  y  \leq 25, i = 2,...,10 \\
+&p_0 = 0\\
+&\Delta p \in [0,2] \\
+\end{align*}
+	The function $flightTime(\textbf{x},\textbf{y})$ is a black-box.
+The values $\textbf{xc}_j$ and  $\textbf{yc}_j$ specify the exclusion zone centers while $\textbf{r}_j$ specify the radii.
+A solution to this problem is shown in figure \ref{fig:FPP}.
+In this figure there are two exclusion zones.
+\begin{figure}[h]
+  \caption{True Pareto Frontier for CTP}
+  \centering
+  \includegraphics[width=0.85\textwidth]{FPP.png}  
+  \label{fig:FPP}
+\end{figure}
+
+\begin{figure}[h]
+  \caption{True Pareto Frontier for CTP}
+  \centering
+  \includegraphics[width=0.85\textwidth]{FPP_pareto.png}  
+  \label{fig:FPP_pareto}
+\end{figure}
 

### 2017-04-24 FlightPathOpt.m

@@ -81,7 +81,7 @@ h_path = plot(PathPoints(:,1),PathPoints(:,2),'k','linewidth',2);
 LineTime = getTimeFromPath(PathPoints,W_x,W_y,AirSpeed);
 fprintf('Travel Time: %d hours, %.1f minutes\n',floor(LineTime),rem(LineTime,1)*60);
 %% Add No Fly Zone
-xc = [5,40,20]; yc = [5,5,20]; radius = [5,10,10];  %Alter these params to get different no-fly zones
+xc = [40,20]; yc = [5,20]; radius = [10,10];  %Alter these params to get different no-fly zones
 for i = 1:length(xc)
     t = linspace(0,2*pi);
     x_bounds = xc(i)+radius(i)*cos(t);

### 2017-04-25 draft1_SM.tex
Update draft1_SM.tex

@@
 Table~\ref{tab:OSY} summarizes the mean quality metrics for each algorithm for ten runs.
-%\begin{figure}[h]
-%  \caption{Example Pareto Results for OSY}
-%  \centering
-%  \includegraphics[width=0.85\textwidth]{OSY_pareto_final.png}  
-%  \label{fig:OSY}
-%\end{figure}
+\begin{figure}[h]
+  \caption{Example Pareto Results for OSY}
+  \centering
+  \includegraphics[width=0.85\textwidth]{OSY_pareto_final.png}  
+  \label{fig:OSY}
+\end{figure}
 
@@
 Metric & MATLABs MOGA & Our MOGA \\ \hline
-CD &  &   \\ \hline
-OS &  &  \\ \hline
+CD & 0.7882 (0.1995) & 0.5507 (0.0685)  \\ \hline
+OS & 0.5322 (0.3393) & 0.9608 (0.2427) \\ \hline
 \end{tabular}
@@
 \end{table}
+
+Overall, our MOGA outperformed MATLABs MOGA in both quality metrics.
+However, by examining the Pareto frontiers, it is clear that neither algorithm is truely satisfactory in estimating the true Pareto frontier.
 

### 2017-04-26 QualityMetrics.m
Add files via upload

@@ -1,0 +1,59 @@
+close all; clear all; clc;
+
+prompt = 'Which problem to Evaluate?  \n 1 - ZDT1\n 2 - ZDT2 \n 3 - ZDT3 \n 4 - OSY \n 5 - TNK \n 6 - CTP \n';
+prob = input(prompt);
+
+for test = 1:10
+   
+    %% ZDT1
+    if prob == 1
+        nChrome = 300; nRun = 100;
+        X_true = zeros(100,30);
+        X_true(:,1) = linspace(0,1,100);
+        true_P = ZDT1(X_true);     
+   %% ZDT2
+   elseif prob == 2
+        nChrome = 300; nRun = 100;
+        X_true = zeros(100,30);
+        X_true(:,1) = linspace(0,1,100);
+        true_P = ZDT2(X_true);
+    %% ZDT3
+   elseif prob == 3
+        nChrome = 300; nRun = 100;
+        X_true = zeros(100,30);
+        X_true(:,1) = linspace(0,1,100);
+        true_P = ZDT3(X_true);
+    %% OSY
+    elseif prob == 4
+        nChrome = 60; nRun = 1000;
+        true_P = [5,-275;75,-45];
+        
+    %% TNK
+    elseif prob == 5
+        nChrome = 40; nRun = 200;
+        true_P = [1,0;0,1];
+    %% CTP
+    elseif prob == 6
+        nChrome = 100; nRun = 100;        
+        true_P = [1,0;0,1];
+    end
+    load(['results_and_params',num2str(prob),'_nChr',num2str(nChrome),'_nRun',num2str(nRun),'_nTest',num2str(test)])
+    
+    
+    figure
+    plot(Fmoga(:,1),Fmoga(:,2),'bo','LineWidth',2);
+    hold on
+    hold on; 
+    plot(Pareto(:,1),Pareto(:,2),'gv','LineWidth',2,'MarkerSize',10)
+%     plot(optF(:,1),optF(:,2),'r*','LineWidth',2)
+    hold on; grid on; legend('MATLABs MOGA','Our MOGA')
+    xlabel('f_1'); ylabel('f_2')
+    
+    CD(test) = coverageDifference2(Pareto);
+    CD_M(test) = coverageDifference2(Fmoga(:,1:2));  
+
[…]

### 2017-04-26 draft1_SM.tex
Update draft1_SM.tex
adding discretized robustness

@@
 \subsection{OSY} 
-This test problem, denoted as OSY in (insert reference) is shown below.
+This test problem, denoted as OSY in (insert reference) is shown below, Figure~\ref{fig:OSY_true} shows the true Pareto frontier for this problem.
 
@@
 \end{align*}
+\begin{figure}[h]
+  \caption{True Pareto Frontier for OSY}
+  \centering
+  \includegraphics[width=0.85\textwidth]{OSY_pareto_true.png}  
+  \label{fig:OSY_true}
+\end{figure}
 
-The true Pareto frontier for this problem again occurs when $x_i$ = 0 for i = 2,...,30.
 Figure~\ref{fig:OSY} shows a sample result from both MATLABs built in MOGA and the MOGA developed in this project.
@@
 
-\section{Flight Planning Problem (FPP)}
+\section{Robust Problems}
+
+\subsection{Robust TNK} 
+This test problem, denoted as TNK in (insert reference) is shown below with the true Pareto frontier shown in Figure~\ref{fig:TNK_true}.
+
+\begin{align*}
+\textrm{Minimize} ~~~~~ f_1(\textbf{x}) &= x_1 \\
+\textrm{Minimize} ~~~~~ f_2(\textbf{x}) &= x_2 \\
+\textrm{Subject to} ~~~~ g_1(x) &= 1+0.1\cos(16\arctan(\frac{x_1}{x_2})) + \\
+&~~~~ 0.2\sin{p_1}\cos{p_2} -x_1^2-x_2^2\leq 0 \\
+g_2(x) &= (x_1 - 0.5)^2 + (x_2 - 0.5)^2 -0.5 \leq 0 \\
+0 &\leq  x_1,x_2 \leq \pi \\
+-1& \leq p \leq 3\\
+\end{align*}
+
+Figure~\ref{fig:robust} shows a sample result from both MATLABs built in MOGA and the robust MOGA developed in this project.
+Table~\ref{tab:robustTNK} summarizes the mean quality metrics for each algorithm for ten runs.
+\begin{figure}[h]
+  \caption{Example Pareto Results for TNK}
+  \centering
+  \includegraphics[width=0.85\textwidth]{prob7_nChr25_nRun400.png}  
+  \label{fig:robustTNK}
+\end{figure}
+
+\begin{table}[h]
+\caption{Quality Metrics for TNK} 
+\centering 
+\begin{tabular}{|c|c|c|} 
+\hline\hline  
+Metric & MATLABs MOGA & Our MOGA \\ \hline
+CD &  0.8581 (0.0480) & 0.7792 (0.0036) \\ \hline
+OS & 0.4177 (0.3216) & 0.9763 (0.0178)\\ \hline
+\end{tabular}
+\label{tab:robustTNK} 
+\end{table}
+
+Comparing the estimated Pareto frontiers to the true Pareto frontier, is is clear that our MOGA outperforms MATLAB's MOGA.
+The Pareto spread in our MOGA is significantly higher however the coverage difference is higher in MATLABs MOGA (p<0.05).
+
+\subsection{Flight Planning Problem (FPP)}
 Now let us consider the final problem where we try to minimize the total flight time from the start location $(0,12.5)$ to the finish location $(40,12.5)$.

### 2017-04-26 FlightPathOpt.m

@@ -81,17 +81,15 @@ h_path = plot(PathPoints(:,1),PathPoints(:,2),'k','linewidth',2);
 LineTime = getTimeFromPath(PathPoints,W_x,W_y,AirSpeed);
 fprintf('Travel Time: %d hours, %.1f minutes\n',floor(LineTime),rem(LineTime,1)*60);
 %% Add No Fly Zone
-xc = [40,20]; yc = [5,20]; radius = [10,10];  %Alter these params to get different no-fly zones
+xc = [40,20]; yc = [5,20]; radius = [7,7];  %Alter these params to get different no-fly zones
+
+
 for i = 1:length(xc)
-    t = linspace(0,2*pi);
-    x_bounds = xc(i)+radius(i)*cos(t);
-    x_bounds(x_bounds >sizeX) = sizeX;
-    x_bounds(x_bounds < 0) =0;
-    y_bounds = yc(i)+radius(i)*sin(t);
-    y_bounds(y_bounds >sizeY) = sizeY;
-    y_bounds(y_bounds < 0) = 0;
-    plot(x_bounds,y_bounds);
+    plotFlightBounds(xc(i),yc(i),radius(i),sizeX,sizeY,'b')
+    plotFlightBounds(xc(i),yc(i),radius(i)+2,sizeX,sizeY,'b.')
 end
+
+
 
 %% Optimization
 % Initial Conditions
@@ -103,6 +101,9 @@ ic = ic(:);
 % Bounds
 lb = zeros(size(ic(:)));
 ub = reshape([sizeX*ones(1,numWayPoints); sizeY*ones(1,numWayPoints)],[],1);
+
+
+
 
 % Define 1st Objective Function
 objectiveFun = @(P) getTimeFromPath(P,W_x,W_y,AirSpeed,sizeX,sizeY,'PCHIP');
@@ -131,6 +132,11 @@ else
     problem_function= @(P) [objectiveFun(P) distanceFromExclusionZone(P)];
 
     %Define Constraint Function
+    %% Maximize The feasibility constraints for robustness.
+    problem_constraints = @(P,radius) min(flightConstraints(P,sizeX,sizeY,xc,yc,radius)); 
+    delta_P = maximumDeltaP([12.5,25],radius,radius+2,problem_constraints);
+    radius = radius+delta_P;
+    %%
     problem_constraints = @(P) flightConstraints(P,sizeX,sizeY,xc,yc,radius); 
[…]

### 2017-04-26 MasterCode.m

@@ -1,6 +1,7 @@
 %function [optX,optF]=MasterCode(prob,nChrome,nRun,alpha_,sigma_,epsilon_,save_figure,use_matlabs_moga)
-% load .mat file
 nargin=0;
+
+% load .mat file
 current_dir = pwd;
 %file_name = 'results_and_params.mat';
 if(contains(current_dir,'/ENME625_Optimization')) %linux or mac
@@ -17,6 +18,7 @@ results_and_params = results_and_params.results_and_params;
 
 global alpha sigma epsilon
 
+%% helper functions 
 if(nargin < 1)
     prompt = 'Which Test Problem Do You Want To Run? \n 1 - ZDT1\n 2 - ZDT2 \n 3 - ZDT3 \n 4 - OSY \n 5 - TNK \n 6 - CTP \n 7 - Robust TNK \n';
     prob = input(prompt);
@@ -75,23 +77,29 @@ switch prob
     case 4
         problem_function = @(X) OSY(X);
         nvar = 6; LB = [0,0,1,0,1,0]; UB = [10,10,5,6,5,10];
-        problem_constraints = @OSY_constraints; % Only used in matlab test
+        problem_constraints = @OSY_constraints; % Only used in matlab MOGA test
     case 5 
         problem_function = @(X) TNK(X);
         nvar = 2; LB = [0,0]; UB=[pi,pi];
-        problem_constraints = @TNK_constraints; % Only used in matlab test
+        problem_constraints = @TNK_constraints; % Only used in matlab MOGA test
 
     case 6
         problem_function = @(X) CTP(X);
         nvar = 10; LB = -5*ones(1,10); UB = 5*ones(1,10); LB(1,1) = 0; UB(1,1) = 1;
-        problem_constraints = @CTP_constraints; % Only used in matlab test
+        problem_constraints = @CTP_constraints; % Only used in matlab MOGA test
     case 7 
         DP=1;
-        problem_function = @(X,DP) TNK_Robust(X,DP);
         nvar = 2; LB = [0,0]; UB=[pi,pi];
-        robust_fitness = @(X,DP) TNK_NEGCN2(X,DP);
+        %Find Maximize DP
+        delta_P = maximumDeltaP([pi/2,pi/2],[-2,-2],[2,2],@TNK_NEGCN2);
+        problem_function = @(X) TNK_Robust(X,delta_P);
+        problem_constraint = @(X) TNK_NEGCN2(X,delta_P); 
[…]

### 2017-04-26 TNK.m

@@ -11,6 +11,6 @@ nconstr = 2*ones(length(X(:,1)),1);
 nconstr_lin = 0*ones(length(X(:,1)),1);
 UNCT = 0*ones(length(X(:,1)),1);
 
-f = [f1,f2,constraint,nfunc,nconstr,nconstr_lin,UNCT];
+f = [f1,f2,constraint,nfunc,nconstr,nconstr_lin];
 
 end

### 2017-04-26 fitFCN5.m

@@ -1,37 +1,7 @@
-function [ fit ] = fitFCN5(X, ZD_func,robust_constraint_fitness)
+function [ fit ] = fitFCN5(X, ZD_func)
 %NSGA algorithm. Use Approach 1 for sorting
 global alpha sigma epsilon
-
-cheat = 1;
-
-if nargin < 3
-    robust_constraint_fitness = [];
-end
-
-%Check is this is a robust problem
-delta_P = [];
-if isempty(robust_constraint_fitness)
-    func = ZD_func(X);
-else%Evaluates feasible solutions with uncertaintly applied in problems with
-%uncertainy
-    if cheat ==1
-        delta_P = [0.5708*ones(length(X),1),-1*ones(length(X),1)];
-    else
-        [M,~] = size(X);
-        for k = 1:M
-            options = optimoptions(@ga,'PopulationSize',10,'UseVectorized',true);
-            lb = [-2,-2]; ub = [2,2];
-            fitnessfn = @(DP) -TNK_NEGCN2(X(k,:),DP);
-            [d_p,~] = ga(fitnessfn,2,[],[],[],[],lb,ub,[],options);
-            delta_P = [delta_P ; d_p];
-        end
-    end
-    func = ZD_func(X,delta_P);
-end
-
-
-
-
+func = ZD_func(X);
 
 % 
 % if isempty(existing_points)

### 2017-04-26 getDistanceExclustionZone.m

@@ -16,5 +16,5 @@ for i = 1:length(radius)
     dist(i) = sqrt(min((PathPoints(:,1) - xc(i)).^2 +(PathPoints(:,2) -yc(i)).^2 ));
 end
 
-constraints = radius' - dist;
+%constraints = radius' - dist;
 %closest_dist = sqrt(min(squared_dist));

### 2017-04-26 maximumDeltaP.m

@@ -1,0 +1,9 @@
+function delta_P = maximumDeltaP(X,lb,ub,constraint_function)
+
+%[x1,x2] = meshgrid(linspace(lb(1),ub(1),20),linspace(lb(2),ub(2),20));
+%X = [x1,x2];
+%Check is this is a robust problem
+options = optimoptions(@ga,'PopulationSize',10,'UseVectorized',true);
+fitnessfn = @(DP) -constraint_function(X,DP);
+[d_p,~] = ga(fitnessfn,2,[],[],[],[],lb,ub,[],options);
+delta_P = [delta_P ; d_p];

### 2017-04-26 FlightPathOpt.m
should have all figures now

@@ -81,7 +81,7 @@ h_path = plot(PathPoints(:,1),PathPoints(:,2),'k','linewidth',2);
 LineTime = getTimeFromPath(PathPoints,W_x,W_y,AirSpeed);
 fprintf('Travel Time: %d hours, %.1f minutes\n',floor(LineTime),rem(LineTime,1)*60);
 %% Add No Fly Zone
-xc = [40,20]; yc = [5,20]; radius = [7,7];  %Alter these params to get different no-fly zones
+xc = [40,20]; yc = [5,20]; radius = [8.5,7.5];  %Alter these params to get different no-fly zones
 
 
 for i = 1:length(xc)
@@ -133,8 +133,9 @@ else
 
     %Define Constraint Function
     %% Maximize The feasibility constraints for robustness.
-    problem_constraints = @(P,radius) min(flightConstraints(P,sizeX,sizeY,xc,yc,radius)); 
-    delta_P = maximumDeltaP([12.5,25],radius,radius+2,problem_constraints);
+    %problem_constraints = @(P,radius) min(flightConstraints(P,sizeX,sizeY,xc,yc,radius)); 
+    %delta_P = maximumDeltaP([12.5,25],radius,radius+2,problem_constraints);
+    delta_P = 2;
     radius = radius+delta_P;
     %%
     problem_constraints = @(P) flightConstraints(P,sizeX,sizeY,xc,yc,radius); 

### 2017-04-27 fitFCN5.m
Update fitFCN5.m

@@ -1,6 +1,6 @@
 function [ fit ] = fitFCN5(X, ZD_func)
 %NSGA algorithm. Use Approach 1 for sorting
-global alpha sigma epsilon
+global alpha sigma epsilon CF1 CF2
 func = ZD_func(X);
 
 % 
@@ -73,9 +73,6 @@ if nconstr == 0 && nconstr_lin ==0
     %% Similarity
     %Assess similarity layer-by-layer, assess in objective space.
 
-%     sigma = 0.158;
-%     epsilon = 0.1;
-%     alpha = 1;
     var_rem = 0;
     F_min = M+epsilon;
     for k = 1:numLayer
@@ -129,8 +126,6 @@ if nconstr == 0 && nconstr_lin ==0
 %% Constraint Handling
 else
     Cmax = 1.2; Cmin = 0.8; r = 0.8*M; 
-    CF1 = 0.01;
-    CF2 = 0.01;
     rank = zeros(1,M);
     
     % Assign moderate rank to all feasible solutions

### 2017-04-27 FlightPathOpt.m
finished FPP

@@ -8,7 +8,7 @@
 %
 
 %% First make some random vector field of wind, and set parameters
-
+ function [FVAL]  = FlightPathOpt
 clear; clf;
 
 AirSpeed = 500;
@@ -81,12 +81,12 @@ h_path = plot(PathPoints(:,1),PathPoints(:,2),'k','linewidth',2);
 LineTime = getTimeFromPath(PathPoints,W_x,W_y,AirSpeed);
 fprintf('Travel Time: %d hours, %.1f minutes\n',floor(LineTime),rem(LineTime,1)*60);
 %% Add No Fly Zone
-xc = [40,20]; yc = [5,20]; radius = [8.5,7.5];  %Alter these params to get different no-fly zones
+xc = [40,20]; yc = [5,20]; radius = [8.3,7.5];  %Alter these params to get different no-fly zones
 
 
 for i = 1:length(xc)
-    plotFlightBounds(xc(i),yc(i),radius(i),sizeX,sizeY,'b')
-    plotFlightBounds(xc(i),yc(i),radius(i)+2,sizeX,sizeY,'b.')
+    plotFlightBounds(xc(i),yc(i),radius(i),sizeX,sizeY,'b');
+    plotFlightBounds(xc(i),yc(i),radius(i)+2,sizeX,sizeY,'b.');
 end
 
 
@@ -124,7 +124,7 @@ if(single_objective == 1)
     optimalWayPoints = fmincon(objectiveFun, ic(:), [],[],[],[],lb,ub,[],opts);
 else
     %% Find an optimal path using GAMultiobh
-    population_size = 20;
+    population_size = 100;
     %Define 2nd Objective Function
     distanceFromExclusionZone =@(P) -0.1*min(getDistanceExclustionZone(P,sizeX,sizeY,xc,yc,radius));
     
@@ -133,14 +133,17 @@ else
 
     %Define Constraint Function
     %% Maximize The feasibility constraints for robustness.
-    %problem_constraints = @(P,radius) min(flightConstraints(P,sizeX,sizeY,xc,yc,radius)); 
-    %delta_P = maximumDeltaP([12.5,25],radius,radius+2,problem_constraints);
-    delta_P = 2;
+    n_constraints = length(radius);
+    for i = 1:n_constraints
+        pop = 10;
+        constraints = @(P,r) radiusConstraint(P,sizeX,sizeY,xc(i),yc(i),r);
+        delta_P(i) = maximumDeltaP([12.5;25],radius(i),[0,2],constraints,pop);
+    end
[…]

### 2017-04-27 coverageDifference2.m

@@ -8,9 +8,14 @@ min_f1 = min(input(:,1)); max_f1 = max(input(:,1));
 min_f2 = min(input(:,2)); max_f2 = max(input(:,2));
 if min_f1<0
     input(:,1) = input(:,1)+abs(min_f1);
+else
+    input(:,1) = input(:,1)-abs(min_f1);
 end
+    
 if min_f2<0
     input(:,2) = input(:,2)+abs(min_f2);
+else
+    input(:,2) = input(:,2)-abs(min_f2);
 end
 %normalize range
 input(:,1) = input(:,1)./(max_f1-abs(min_f1));

### 2017-04-27 maximumDeltaP.m

@@ -1,9 +1,21 @@
-function delta_P = maximumDeltaP(X,lb,ub,constraint_function)
+% function delta_P = maximumDeltaP(X,lb,ub,constraint_function)
+% 
+% %[x1,x2] = meshgrid(linspace(lb(1),ub(1),20),linspace(lb(2),ub(2),20));
+% %X = [x1,x2];
+% %Check is this is a robust problem
+% options = optimoptions(@ga,'PopulationSize',10,'UseVectorized',true);
+% fitnessfn = @(DP) -constraint_function(X,DP);
+% [d_p,~] = ga(fitnessfn,2,[],[],[],[],lb,ub,[],options);
+% delta_P = [delta_P ; d_p];
 
+
+
+function delta_P = maximumDeltaP(X,p0,bounds,constraint_function,pop)
+lb = bounds(:,1);
+ub = bounds(:,2);
 %[x1,x2] = meshgrid(linspace(lb(1),ub(1),20),linspace(lb(2),ub(2),20));
 %X = [x1,x2];
 %Check is this is a robust problem
-options = optimoptions(@ga,'PopulationSize',10,'UseVectorized',true);
-fitnessfn = @(DP) -constraint_function(X,DP);
-[d_p,~] = ga(fitnessfn,2,[],[],[],[],lb,ub,[],options);
-delta_P = [delta_P ; d_p];
+options = optimoptions(@ga,'PopulationSize',pop,'UseVectorized',true);
+fitnessfn = @(DP) constraint_function(X,DP+p0);
+[delta_P,~] = ga(fitnessfn,length(lb),[],[],[],[],lb,ub,[],options);

### 2017-04-27 radiusConstraint.m

@@ -1,0 +1,19 @@
+function dist = radiusConstraint(PathPoints,sizeX,sizeY,xc,yc,radius)
+% Tell you how close you will get to the exclusion zones with a path.  
+% returns a value for each exclusion zone
+
+METHOD = 'PCHIP';
+%Convert waypooints to path
+if isvector(PathPoints)
+    PathPoints = [0 sizeY/2; reshape(PathPoints,2,[])'; sizeX sizeY/2];
+    PathPoints = WayPoints_To_Path(PathPoints,METHOD,sizeX,sizeY,101);
+end
+
+dist = zeros(length(PathPoints),length(radius));
+
+for i = 1:length(radius)
+    dist(:,i) =  sqrt((PathPoints(:,1) - xc).^2 +(PathPoints(:,2) -yc).^2 ) - radius(i);
+end
+dist = min(dist,[],1);
+%constraints = radius' - dist;
+%closest_dist = sqrt(min(squared_dist));

### 2017-04-27 MasterCode.m
everything working now

@@ -91,7 +91,10 @@ switch prob
         DP=1;
         nvar = 2; LB = [0,0]; UB=[pi,pi];
         %Find Maximize DP
-        delta_P = maximumDeltaP([pi/2,pi/2],[-2,-2],[2,2],@TNK_NEGCN2);
+        X = [pi/2,pi/2]; pop=20;
+        constraint_function = @(X,DP) -robust_TNK_constraints(X,DP);
+        delta_P = maximumDeltaP(X,[1.0,1.0],[-2,2;-2,2],constraint_function,pop);
+        %delta_P = maximumDeltaP([pi/2,pi/2],[-2,-2],[2,2],@TNK_NEGCN2);
         problem_function = @(X) TNK_Robust(X,delta_P);
         problem_constraint = @(X) TNK_NEGCN2(X,delta_P); 
     case 8

### 2017-04-27 TNK_Robust.m

@@ -4,7 +4,7 @@ function [f,constraint] = TNK_Robust(X,DP)
 
 f1 = X(:,1);
 f2 = X(:,2);
-g1 = 1  +0.1*cos(16*atan2(X(:,1),X(:,2)))+0.2*sin(DP(:,1)+1).*cos(DP(:,2)+1) - X(:,1).^2 -X(:,2).^2;
+g1 = 1  +0.1*cos(16*atan2(X(:,1),X(:,2)))+0.2*sin(DP(:,1)).*cos(DP(:,2)) - X(:,1).^2 -X(:,2).^2;
 g2 = (X(:,1)-0.5).^2 + (X(:,2)-0.5).^2 -0.5;
 constraint = [g1 g2];
 

### 2017-04-27 robust_TNK_constraints.m

@@ -1,0 +1,5 @@
+function [constraints] = robust_TNK_constraints(X,DP)
+g1 = 1  +0.1*cos(16*atan2(X(:,1),X(:,2)))+0.2*sin(DP(:,1)).*cos(DP(:,2)) - X(:,1).^2 -X(:,2).^2;
+g2 = (X(:,1)-0.5).^2 + (X(:,2)-0.5).^2 -0.5;
+
+constraints = [g1];  % ignoring g2 because it is not a function of p

### 2017-04-27 fitFCN2.m
removing old code

@@ -1,100 +1,0 @@
-function [ fit ] = fitFCN2(X, ZD_func, V)
-%NSGA algorithm. Use Approach 1 for sorting
-%global func nfunc V
-
-func = ZD_func(X);
-nfunc = length(func);
-
-
-chrome = V;
-%% Find Dominate Points
-% Modify existing code to find Pareto points to find dominant layers
-
-P_temp = func;
-Pprime = func;
-level = 1;
-func(:,nfunc+1) = 0;
-while ~isempty(P_temp)
-    if length(P_temp(:,1))== 1        
-        break 
-    end
-    [~,place] = prtp(P_temp);
-    q = 0; m = 1;
-    for k = 1:length(place)
-        marker= find(P_temp(place(k),1)==func(:,1));
-        func(marker,nfunc+1) = level; marker= [];
-    end
-    level = level+1;
-    P_temp(place,:) = []; place = []; 
-end
-
-  
-numLayer = level-1; 
-
-%Make sure all variables have a layer number
-flag = 0;
-for k = 1:chrome
-    if func(nfunc+1)==0
-        func(k,nfunc+1) = numLayer+1;
-        flag = 1;
-    end
-end
-if flag == 1, numLayer = numLayer+1; end
-    
-%% Similarity
-%Assess similarity layer-by-layer, assess in objective space.
-sigma = 0.75;
-epsilon = 0.25;
-alpha = 5;
-
-F_min = chrome+epsilon;
-for k = 1:numLayer
-    Fitness = []; incl = [];
- 
-    incl = find(func(:,nfunc+1)==k);
-    Fitness = func(incl,:);
-    
-    if length(incl) == 1
-        d = 0;
-        sh = 1;
-        nc = 1;
-        Fit_share = (F_min-epsilon)/nc;
-        F_min = min(Fit_share);
-        func(incl,nfunc+2) = Fit_share;
-    else
-        for m = 1:nfunc
-            maxF(m) = max(Fitness(:,m));
-            minF(m) = min(Fitness(:,m));
-        end      
-        d = []; similar = [];
-        for i = 1:length(incl)
-            F_int = F_min-epsilon;
-            for j = 1:length(incl)   
-                for k = 1:nfunc
-                    similar(k) = ((Fitness(i,k)-Fitness(j,k))/(maxF(k)-minF(k)))^2;
-                end
-                d(i,j) = sqrt(sum(similar));
-               if d(i,j)<=sigma
[…]

### 2017-04-27 fitFCN3.m

@@ -1,123 +1,0 @@
-function [ fit ] = fitFCN3( pop)
-%NSGA algorithm. Use Approach 1 for sorting
-global V prob w1 w2
-
-
-if prob == 1
-    %% ZDT1
-    F1 = pop(1);
-    g = 1+(9/(V-1))*sum(pop(2:end));
-    h = 1- sqrt(F1/g);
-    F2 = g*h;
-    func = [w1*F1,w2*F2];
-    nfunc = 2;
-
-elseif prob == 2
-    %% ZDT2
-    F1 = pop(1);
-    g = 1+(9/(V-1))*sum(pop(2:end));
-    h = 1- (F1/g)^2;
-    F2 = g*h;
-    func = [F1,F2];
-    nfunc = 2;
-elseif prob == 3
-    %% ZDT3
-    F1 = pop(1);
-    g = 1+(9/(V-1))*sum(pop(2:end));
-    h = 1- sqrt(F1/g) - (F1/g)*sin(10*pi*F1);
-    F2 = g*h;
-    func = [F1,F2];
-    nfunc = 2;
-
-end
-
-chrome = V;
-%% Find Dominate Points
-% Modify existing code to find Pareto points to find dominant layers
-
-P_temp = func;
-Pprime = func;
-level = 1;
-func(:,nfunc+1) = 0;
-while ~isempty(P_temp)
-    if length(P_temp(:,1))== 1        
-        break 
-    end
-    [~,place] = prtp(P_temp);
-    q = 0; m = 1;
-    for k = 1:length(place)
-        marker= find(P_temp(place(k),1)==func(:,1));
-        func(marker,nfunc+1) = level; marker= [];
-    end
-    level = level+1;
-    P_temp(place,:) = []; place = []; 
-end
-
-  
-numLayer = level-1; 
-
-%Make sure all variables have a layer number
-flag = 0;
-for k = 1:chrome
-    if func(nfunc+1)==0
-        func(k,nfunc+1) = numLayer+1;
-        flag = 1;
-    end
-end
-if flag == 1, numLayer = numLayer+1; end
-    
-%% Similarity
-%Assess similarity layer-by-layer, assess in objective space.
-sigma = 0.75;
-epsilon = 0.25;
-alpha = 5;
-
-F_min = chrome+epsilon;
-for k = 1:numLayer
-    Fitness = []; incl = [];
- 
-    incl = find(func(:,nfunc+1)==k);
-    Fitness = func(incl,:);
[…]

### 2017-04-27 fitFCN4.m

@@ -1,116 +1,0 @@
-function [ fit ,func] = fitFCN4(X, ZD_func, V,existing_points)
-%NSGA algorithm. Use Approach 1 for sorting
-%global func nfunc V
-
-%func = ZD_func(X);
-
-if isempty(existing_points)
-    fit = sum(ZD_func(X));
-    return 
-end
-
-%% Find Dominate Points
-% Modify existing code to find Pareto points to find dominant layers
-
-func = [existing_points;ZD_func(X)];
-[nvar,nfunc] = size(func);
-level = 0;
-level_col = nfunc +2;
-nc_col = nfunc + 3;
-init_fit_col = nfunc + 4;
-sim_col = nfunc+5;
-indecies = [1:nvar]';
-func = [func,indecies]; %We need to know indecies later so this should save time
-P_temp = func;
-func(:,level_col) = 0;
-%
-while ~isempty(P_temp)
-    level = level+1;% increment the level value
-    if length(P_temp(:,1))== 1
-        %If there is only one value left at the end, assign this to a level
-        func(P_temp(:,nfunc+1),level_col) = level;
-        break 
-    end
-    [~,place] = prtp(P_temp(:,1:nfunc)); % get all the indecies in the lowest layer
-    current_level_indecies = P_temp(place,nfunc+1); %map them from
-    func(current_level_indecies, level_col) = level; % assiged from prtp
-    P_temp(place, :) = [];
-end
-
-  
-numLayer = level; 
-
-%Make sure all variables have a layer number
-%flag = 0;
-%for k = 1:nvar
-%    if func(level_col)==0
-%        func(k,level_col) = numLayer+1;
-%        flag = 1;
-%    end
-%end
-%if flag == 1, numLayer = numLayer+1; end
-    
-%% Similarity
-%Assess similarity layer-by-layer, assess in objective space.
-sigma = 0.75;
-epsilon = 0.25;
-alpha = 1;
-var_rem = 0;
-F_min = nvar+epsilon;
-for layer = 1:numLayer
-    Fitness = []; incl = [];
-    
-    F_min = length(func(:,1))+epsilon-var_rem;
-    incl = find(func(:,level_col)==layer);
-    Fitness = func(incl,1:nfunc);
-    var_rem = var_rem+length(Fitness(:,1));
-    if(isempty(Fitness) == 0)
-        if length(incl) == 1
-            d = 0;
-            sh = 1;
-            nc = 1;
[…]

### 2017-04-27 fitFCN6.m

@@ -1,24 +1,0 @@
-function [ fit ] = fitFCN6(X, ZD_func,existing_points)
-%NSGA algorithm. Use Approach 1 for sorting
-
-
-possible_points = ZD_func(X);
-
-[rows,cols] = size(possible_points);
-
-
-if isempty(existing_points)
-    fit = sum(possible_points,2);
-    return
-end
-
-fit = zeros(rows,1);
-for i = 1:rows
-    new_point = possible_points(i,:);
-    fit(i,1) = -getFitness(existing_points,new_point);
-end
-return
-    
-    
-    
-    

### 2017-04-27 fitFCN7.m

@@ -1,120 +1,0 @@
-function [ fit ] = fitFCN7(X, ZD_func)
-%NSGA algorithm. Use Approach 1 for sorting
-
-[func,g ] = ZD_func(X);
-val = addConstraints(g);
-func = func + [val val] ;
-% 
-% if isempty(existing_points)
-%     fit = sum(ZD_func(X));
-%     return 
-% end
-
-%% Find Dominate Points
-
-% Modify existing code to find Pareto points to find dominant layers
-
-% func = [existing_points;ZD_func(X)];
-[nvar,nfunc] = size(func);
-level = 0;
-level_col = nfunc +2;
-nc_col = nfunc + 3;
-init_fit_col = nfunc + 4;
-sim_col = nfunc+5;
-indecies = [1:nvar]';
-func = [func,indecies]; %We need to know indecies later so this should save time
-P_temp = func;
-func(:,level_col) = 0;
-%
-while ~isempty(P_temp)
-    level = level+1;% increment the level value
-    if length(P_temp(:,1))== 1
-        %If there is only one value left at the end, assign this to a level
-        func(P_temp(:,nfunc+1),level_col) = level;
-        break 
-    end
-    place = paretoset(P_temp(:,1:nfunc)); % get all the indecies in the lowest layer
-    for k = 1:length(place)
-        if place(k) == 1
-            current_level_indecies = P_temp(k,nfunc+1); %map them from
-            func(current_level_indecies, level_col) = level; % assiged from prtp
-        end
-    end     
-    
-    P_temp(place, :) = [];
-end
-
-  
-numLayer = level; 
-
-%Make sure all variables have a layer number
-flag = 0;
-for k = 1:nvar
-   if func(level_col)==0
-       func(k,level_col) = numLayer+1;
-       flag = 1;
-   end
-end
-if flag == 1, numLayer = numLayer+1; end
-    
-%% Similarity
-%Assess similarity layer-by-layer, assess in objective space.
-sigma = 0.75;
-epsilon = 0.25;
-alpha = 1;
-var_rem = 0;
-F_min = nvar+epsilon;
-for k = 1:numLayer
-    Fitness = []; incl = []; 
-    incl = find(func(:,level_col)==k);
-    Fitness = func(incl,1:nfunc);
-    var_rem = var_rem+length(Fitness(:,1));
-    if(isempty(Fitness) == 0)
-        if length(incl) == 1
-            
-            F_int = F_min-epsilon;
[…]

### 2017-04-27 fitFCN8.m

@@ -1,242 +1,0 @@
-function [ fit ] = fitFCN8(X, ZD_func,existing_points)
-%NSGA algorithm. Use Approach 1 for sorting
-
-func = ZD_func(X);
-
-% 
-% if isempty(existing_points)
-%     fit = sum(ZD_func(X));
-%     return 
-% end
-
-%% Find Dominate Points
-
-% Modify existing code to find Pareto points to find dominant layers
-
-% func = [existing_points;ZD_func(X)];
-nfunc = func(1,end-2);
-nconstr = func(1,end-1);
-g = func(:,nfunc+1:nfunc+nconstr);
-nconstr_lin = func(1,end);
-h = func(:,nfunc+nconstr+1:nfunc+nconstr+nconstr_lin);
-func = func(:,1:nfunc);
-
-[M,~] = size(X);
-
-
-
-
-if nconstr == 0 && nconstr_lin ==0
-    nc_col = nfunc + 3;
-    init_fit_col = nfunc + 4;
-    sim_col = nfunc+5;
-    indecies = [1:M]';
-    func = [func,indecies]; %We need to know indecies later so this should save time
-    P_temp = func;
-    level = 0;
-    level_col = nfunc +2;
-    func(:,level_col) = 0;
-    while ~isempty(P_temp)
-        level = level+1;% increment the level value
-        if length(P_temp(:,1))== 1
-            %If there is only one value left at the end, assign this to a level
-            func(P_temp(:,nfunc+1),level_col) = level;
-            break 
-        end
-        place = paretoset(P_temp(:,1:nfunc)); % get all the indecies in the lowest layer
-        for k = 1:length(place)
-            if place(k) == 1
-                current_level_indecies = P_temp(k,nfunc+1); %map them from
-                func(current_level_indecies, level_col) = level; % assiged from prtp
-            end
-        end     
-
-        P_temp(place, :) = [];
-    end
-
-    numLayer = level; 
-
-    %Make sure all individuals have a layer number
-    flag = 0;
-    for k = 1:M
-       if func(level_col)==0
-           func(k,level_col) = numLayer+1;
-           flag = 1;
-       end
-    end
-    if flag == 1, numLayer = numLayer+1; end
-
-    %% Similarity
-    %Assess similarity layer-by-layer, assess in objective space.
-
-    sigma = 0.75;
-    epsilon = 0.25;
-    alpha = 1;
-    var_rem = 0;
-    F_min = M+epsilon;
-    for k = 1:numLayer
[…]

### 2017-04-27 MasterCode.m
adding CF1/2 as a var

@@ -16,7 +16,10 @@ file_name = [path_prefix,'results_and_params.mat'];
 results_and_params = load(file_name);
 results_and_params = results_and_params.results_and_params;
 
-global alpha sigma epsilon
+global alpha sigma epsilon CF1 CF2
+
+CF1 = 0.01;
+CF2 = 0.01;
 
 %% helper functions 
 if(nargin < 1)

### 2017-05-03 CTP.m
Fully running code (on my computer)

@@ -1,8 +1,10 @@
-function [f,constraint] = CTP(X)
+function [f] = CTP(X)
+
+global Mmoga
 
 f1 = X(:,1);
-G = 1+ sum(X(:,2:end),2).^0.25;
-f2 = G.*(1-sqrt(f1/G));
+G = abs(1+ sum(X(:,2:end),2).^0.25);
+f2 = G.*(1-sqrt(f1./G));
 theta = -0.2*pi;
 a = 0.2;
 b=10;
@@ -16,9 +18,12 @@ constraint = right_ineq-left_ineq;
 
 nfunc = 2*ones(length(X(:,1)),1);
 nconstr = 1*ones(length(X(:,1)),1);
-nconstr_lin = 0*ones(length(X(:,1)),1);
+nconstr_eq = 0*ones(length(X(:,1)),1);
 UNCT = 0*ones(length(X(:,1)),1);
 
-f = [f1,f2,constraint,nfunc,nconstr,nconstr_lin,UNCT];
-
+if Mmoga == 0
+    f = [f1,f2,constraint,nfunc,nconstr,nconstr_eq,UNCT];
+else 
+    f = [f1,f2];
+end
 end

### 2017-05-03 coverageDifference2.m

@@ -8,14 +8,9 @@ min_f1 = min(input(:,1)); max_f1 = max(input(:,1));
 min_f2 = min(input(:,2)); max_f2 = max(input(:,2));
 if min_f1<0
     input(:,1) = input(:,1)+abs(min_f1);
-else
-    input(:,1) = input(:,1)-abs(min_f1);
 end
-    
 if min_f2<0
     input(:,2) = input(:,2)+abs(min_f2);
-else
-    input(:,2) = input(:,2)-abs(min_f2);
 end
 %normalize range
 input(:,1) = input(:,1)./(max_f1-abs(min_f1));

### 2017-05-03 fitFCN5.m

@@ -1,13 +1,8 @@
 function [ fit ] = fitFCN5(X, ZD_func)
 %NSGA algorithm. Use Approach 1 for sorting
+
 global alpha sigma epsilon CF1 CF2
 func = ZD_func(X);
-
-% 
-% if isempty(existing_points)
-%     fit = sum(ZD_func(X));
-%     return 
-% end
 
 %% Find Dominate Points
 
@@ -15,14 +10,13 @@ func = ZD_func(X);
 
 % func = [existing_points;ZD_func(X)];
 
+XOLin = X;
+UNCT = func(1,end);
 nfunc = func(1,end-3);
 nconstr = func(1,end-2);
 g = func(:,nfunc+1:nfunc+nconstr);
-nconstr_lin = func(1,end-1);
-if nconstr_lin > 0
-    fprintf('weird error here')
-end
-h = func(:,nfunc+nconstr+1:nfunc+nconstr+nconstr_lin);
+nconstr_eq = func(1,end-1);
+h = func(:,nfunc+nconstr+1:nfunc+nconstr+nconstr_eq);
 func = func(:,1:nfunc);
 
 [M,~] = size(X);
@@ -30,7 +24,7 @@ func = func(:,1:nfunc);
 
 
 
-if nconstr == 0 && nconstr_lin ==0
+if nconstr == 0 && nconstr_eq ==0
     nc_col = nfunc + 3;
     init_fit_col = nfunc + 4;
     sim_col = nfunc+5;
@@ -72,7 +66,6 @@ if nconstr == 0 && nconstr_lin ==0
 
     %% Similarity
     %Assess similarity layer-by-layer, assess in objective space.
-
     var_rem = 0;
     F_min = M+epsilon;
     for k = 1:numLayer
@@ -134,7 +127,7 @@ else
         for p = 1:nconstr
             if g(k,p)>0, flag = 1;
             end
-            if nconstr_lin ~= 0
+            if nconstr_eq ~= 0
                 if h(k,p)~=0, flag_lin = 1;
                 end            
             end            
@@ -144,7 +137,26 @@ else
         end
      end
     
-
+     %Evaluates feasible solutions with uncertaintly applied in problems with
+    %uncertainy
+     if UNCT == 1
+         for k = 1:M
+             if rank(k) == 0.5*M
+                 options = optimoptions(@ga,'PopulationSize',10,'UseVectorized',true);
+                 lb = -2; ub = 2;
[…]

### 2017-05-03 FlightPathOpt.m
changable seed

@@ -8,8 +8,8 @@
 %
 
 %% First make some random vector field of wind, and set parameters
- function [FVAL]  = FlightPathOpt
-clear; clf;
+ function [FVAL]  = FlightPathOpt(seed)
+clf;
 
 AirSpeed = 500;
 sizeX = 50;
@@ -81,6 +81,7 @@ h_path = plot(PathPoints(:,1),PathPoints(:,2),'k','linewidth',2);
 LineTime = getTimeFromPath(PathPoints,W_x,W_y,AirSpeed);
 fprintf('Travel Time: %d hours, %.1f minutes\n',floor(LineTime),rem(LineTime,1)*60);
 %% Add No Fly Zone
+rng(seed);
 xc = [40,20]; yc = [5,20]; radius = [8.3,7.5];  %Alter these params to get different no-fly zones
 
 

### 2017-05-03 TNK_Robust.m
Add files via upload
Adjusted ENME_parta to include both robust problems. The unconstrained problems are running incredibly slow for some reason and I'm trouble-shooting to figure out way. Could be because of mismatches in files. Other problems work ok.

@@ -1,18 +1,22 @@
 %For incorporation into exisiting code
-function [f,constraint] = TNK_Robust(X,DP)
+function [f,constraint] = TNK_Robust(X)
 
+global Mmoga DP
 
 f1 = X(:,1);
 f2 = X(:,2);
-g1 = 1  +0.1*cos(16*atan2(X(:,1),X(:,2)))+0.2*sin(DP(:,1)).*cos(DP(:,2)) - X(:,1).^2 -X(:,2).^2;
+g1 = 1  +0.1*cos(16*atan2(X(:,1),X(:,2)))+0.2*sin(1+DP(:,1)).*cos(1+DP(:,2)) - X(:,1).^2 -X(:,2).^2;
 g2 = (X(:,1)-0.5).^2 + (X(:,2)-0.5).^2 -0.5;
 constraint = [g1 g2];
 
 nfunc = 2*ones(length(X(:,1)),1);
 nconstr = 2*ones(length(X(:,1)),1);
 nconstr_lin = 0*ones(length(X(:,1)),1);
-UNCT = 1*ones(length(X(:,1)),1);
+UNCT = 0*ones(length(X(:,1)),1);
 
-f = [f1,f2,constraint,nfunc,nconstr,nconstr_lin,UNCT];
-
+if Mmoga == 0,
+    f = [f1,f2,constraint,nfunc,nconstr,nconstr_lin,UNCT];
+else
+    f = [f1,f2];
+end
 end

### 2017-05-03 ZDT1.m

@@ -1,18 +1,23 @@
 function [ f ] = ZDT1( X )
 %ZDT1 - First test problem from Deb
-
+global Mmoga
 nvar = length(X(1,:));
-F1 = X(:,1);
+f1 = X(:,1);
 
 g = 1+(9./(nvar-1)).*sum(X(:,2:end),2);
-h = 1- sqrt(F1./g);
-F2 = g.*h;
+h = 1- sqrt(f1./g);
+f2 = g.*h;
+
 nfunc = 2*ones(length(X(:,1)),1);
 nconstr = 0*ones(length(X(:,1)),1);
 nconstr_lin = 0*ones(length(X(:,1)),1);
 UNCT = 0*ones(length(X(:,1)),1);
 
-f = [F1,F2,nfunc,nconstr,nconstr_lin,UNCT];
 
+if Mmoga == 0
+    f = [f1,f2,[],nfunc,nconstr,nconstr_lin,UNCT];
+else
+    f = [f1,f2];
+end
 end
 

### 2017-05-04 ZDT1.m
Delete ZDT1.m

@@ -1,23 +1,0 @@
-function [ f ] = ZDT1( X )
-%ZDT1 - First test problem from Deb
-global Mmoga
-nvar = length(X(1,:));
-f1 = X(:,1);
-
-g = 1+(9./(nvar-1)).*sum(X(:,2:end),2);
-h = 1- sqrt(f1./g);
-f2 = g.*h;
-
-nfunc = 2*ones(length(X(:,1)),1);
-nconstr = 0*ones(length(X(:,1)),1);
-nconstr_lin = 0*ones(length(X(:,1)),1);
-UNCT = 0*ones(length(X(:,1)),1);
-
-
-if Mmoga == 0
-    f = [f1,f2,[],nfunc,nconstr,nconstr_lin,UNCT];
-else
-    f = [f1,f2];
-end
-end
-

### 2017-05-04 ZDT1.m
Add files via upload

@@ -1,0 +1,18 @@
+function [ f ] = ZDT1( X )
+%ZDT1 - First test problem from Deb
+
+nvar = length(X(1,:));
+F1 = X(:,1);
+
+g = 1+(9./(nvar-1)).*sum(X(:,2:end),2);
+h = 1- sqrt(F1./g);
+F2 = g.*h;
+nfunc = 2*ones(length(X(:,1)),1);
+nconstr = 0*ones(length(X(:,1)),1);
+nconstr_lin = 0*ones(length(X(:,1)),1);
+UNCT = 0*ones(length(X(:,1)),1);
+
+f = [F1,F2,nfunc,nconstr,nconstr_lin,UNCT];
+
+end
+

### 2017-05-04 ENME625_parta.m
trying to get things working better

@@ -1,5 +1,5 @@
 clear all; close all; clc; warning off;
-
+rng(4)
 global alpha sigma epsilon Mmoga CF1 CF2
 
 prompt2 = 'Run full code or see results only? \n 1 - Run Full Code \n 2 - Results only \n';
@@ -7,6 +7,8 @@ runType = input(prompt2);
 
 prompt = 'Which Test Problem Do You Want To Run? \n 1 - ZDT1\n 2 - ZDT2 \n 3 - ZDT3 \n 4 - OSY \n 5 - TNK \n 6 - CTP \n';
 prob = input(prompt);
+
+runType =1; prob = 5;
 
 %% Load Selected Problem and Optimization Parameters
 switch prob
@@ -46,27 +48,39 @@ end
 if runType == 1
     %% Matlab's MOGA
 
-    options = optimoptions('gamultiobj','PopulationSize', nChrome,'CrossoverFcn', @crossoverscattered,'Display', 'final','PlotFcn', { @gaplotpareto },'ParetoFraction', 0.9);
+    options = optimoptions('gamultiobj','PopulationSize', nChrome,'CrossoverFcn', @crossoverscattered,'ParetoFraction', 0.9,'MaxGenerations',400,'FunctionTolerance',0.000000000000001);
     Mmoga = 1;
     [Xmoga,Fmoga] = gamultiobj(problem_function,nvar,A,b,Aeq,beq,LB,UB,problem_constraints,options);
-    Mmoga = 0;
-
+    
     figure
     plot(Fmoga(:,1),Fmoga(:,2),'bo','LineWidth',2);
     hold on
+    Mmoga = 0;
+
+%nChrome
+%nChrome =200;
 
     %% Our MOGA
     Pareto = [];
-    options = optimoptions(@ga,'PopulationSize',nChrome,'UseVectorized',true,'CrossoverFraction', 0.90);
-    optF =[]; optX = [];
-    for gen = 1:nRun
-        Obj_fcn = @(X) fitFCN5(X,problem_function);
-        [X,fval,exitflag,output] = ga(Obj_fcn,nvar,A,b,Aeq,beq,LB,UB,[],options);
-        [optF(gen,:)] = problem_function(X);
-        optX(gen,:) = X;
-    end
-    nfunc = optF(1,end-3);
-
[…]

### 2017-05-04 NSGA.m

@@ -1,0 +1,100 @@
+    
+function fit = NSGA(func)
+nfunc = 2;
+global alpha sigma epsilon
+
+if isempty(alpha); alpha = 1; end
+if isempty(sigma); sigma = 0.158; end
+if isempty(epsilon); epsilon = 0.22; end
+
+nc_col = nfunc + 3;
+init_fit_col = nfunc + 4;
+sim_col = nfunc+5;
+[M,~] = size(func);
+indecies = [1:M]';
+func = [func,indecies]; %We need to know indecies later so this should save time
+P_temp = func;
+level = 0;
+level_col = nfunc +2;
+func(:,level_col) = 0;
+while ~isempty(P_temp)
+    level = level+1;% increment the level value
+    if length(P_temp(:,1))== 1
+        %If there is only one value left at the end, assign this to a level
+        func(P_temp(:,nfunc+1),level_col) = level;
+        break
+    end
+    place = paretoset(P_temp(:,1:nfunc)); % get all the indecies in the lowest layer
+    for k = 1:length(place)
+        if place(k) == 1
+            current_level_indecies = P_temp(k,nfunc+1); %map them from
+            func(current_level_indecies, level_col) = level; % assiged from prtp
+        end
+    end
+    
+    P_temp(place, :) = [];
+end
+
+numLayer = level;
+
+%Make sure all individuals have a layer number
+flag = 0;
+for k = 1:M
+    if func(level_col)==0
+        func(k,level_col) = numLayer+1;
+        flag = 1;
+    end
+end
+if flag == 1, numLayer = numLayer+1; end
+
+%% Similarity
+%Assess similarity layer-by-layer, assess in objective space.
+var_rem = 0;
+F_min = M+epsilon;
+for k = 1:numLayer
+    Fitness = []; incl = [];
+    incl = find(func(:,level_col)==k); % incl = include
+    Fitness = func(incl,1:nfunc);
+    var_rem = var_rem+length(Fitness(:,1));
+    if(isempty(Fitness) == 0)
+        if length(incl) == 1
+            
+            F_int = F_min-epsilon;
+            Fit_share = F_int;
+            func(incl,sim_col+1) = F_int;
+            func(incl,sim_col) = F_int;
+            func(incl,nc_col) = 1;
+        else
+            for m = 1:nfunc
+                maxF(m) = max(Fitness(:,m));
+                minF(m) = min(Fitness(:,m));
+                func(m,init_fit_col) = minF(m);
+            end
+            d = []; similar = []; sh = [];
[…]

### 2017-05-04 fitFCN5.m

@@ -14,131 +14,47 @@ XOLin = X;
 UNCT = func(1,end);
 nfunc = func(1,end-3);
 nconstr = func(1,end-2);
-g = func(:,nfunc+1:nfunc+nconstr);
+inequality_constraints = func(:,nfunc+1:nfunc+nconstr);
 nconstr_eq = func(1,end-1);
-h = func(:,nfunc+nconstr+1:nfunc+nconstr+nconstr_eq);
+equality_constraints = func(:,nfunc+nconstr+1:nfunc+nconstr+nconstr_eq);
 func = func(:,1:nfunc);
 
 [M,~] = size(X);
 
 
 
-
+%% If there are no 
 if nconstr == 0 && nconstr_eq ==0
-    nc_col = nfunc + 3;
-    init_fit_col = nfunc + 4;
-    sim_col = nfunc+5;
-    indecies = [1:M]';
-    func = [func,indecies]; %We need to know indecies later so this should save time
-    P_temp = func;
-    level = 0;
-    level_col = nfunc +2;
-    func(:,level_col) = 0;
-    while ~isempty(P_temp)
-        level = level+1;% increment the level value
-        if length(P_temp(:,1))== 1
-            %If there is only one value left at the end, assign this to a level
-            func(P_temp(:,nfunc+1),level_col) = level;
-            break 
-        end
-        place = paretoset(P_temp(:,1:nfunc)); % get all the indecies in the lowest layer
-        for k = 1:length(place)
-            if place(k) == 1
-                current_level_indecies = P_temp(k,nfunc+1); %map them from
-                func(current_level_indecies, level_col) = level; % assiged from prtp
-            end
-        end     
-
-        P_temp(place, :) = [];
-    end
-
-    numLayer = level; 
-
-    %Make sure all individuals have a layer number
-    flag = 0;
-    for k = 1:M
-       if func(level_col)==0
-           func(k,level_col) = numLayer+1;
-           flag = 1;
-       end
-    end
-    if flag == 1, numLayer = numLayer+1; end
-
-    %% Similarity
-    %Assess similarity layer-by-layer, assess in objective space.
-    var_rem = 0;
-    F_min = M+epsilon;
-    for k = 1:numLayer
-        Fitness = []; incl = []; 
-        incl = find(func(:,level_col)==k); % incl = include
-        Fitness = func(incl,1:nfunc);
-        var_rem = var_rem+length(Fitness(:,1));
-        if(isempty(Fitness) == 0)
[…]

### 2017-05-05 draft1_SM.tex
here is the more recent draft
Updated Report

@@
 
-\title{Sections and Chapters}
-\author{Gubert Farnsworth}
-\date{ ENME 625: Multi-Displinary Optimization \\ 5/12/2017}
+\title{ENME 625 \\
+Multi-Objective Optimization with Genetic Algorithms}
+\author{Ben Knisely, Stephanie Martin, Jeff Twigg}
+\date{ \today }
 
@@
 
-This is the first section.
+This report develops multi-objective optimization methods using genetic algorithms.
+Three cases of multi-objective optimization are considered: unconstrained optimization, constrained optimization, and robust optimization.
+A fitness function for the first two cases was developed using the built-in MATLAB 'ga' routine.
+The last case was developed such that uncertainty in function parameters could be handled and robustly optimized against.
+
+\noindent Each method developed was evaluated through the use of well-known test problems.
+The resulting Pareto frontier of each method was evaulated in terms of quality metrics.
+Finally, the results of the developed methods were compared to results obtained by using the built-in MATLAB 'gamultiobj' routine.
 
 \section{Unconstrained MOGA Problems}
-We used this textbook \cite{deb2001multi}
+The method by which fitness was assigned to each individual within a population was the well-known Non-dominated Sorting Genetic Algorithm (NSGA), which is fully described in \cite{deb2001multi}.
+For brevity, the full algorithm will not be described here, however the method shall be discussed.
+\newline
+
+\noindent NSGA evaluates the fitness of a population in the follow manner: first the current population is sorted into non-dominated layers.
+This may be accomplished in many ways, however the method used for this project was to continuously update the comparison population.
+That is, once a non-dominated layer is found, these population points are removed from the sorting algorithm and the next non-dominated layer is identified.
+\newline
+
+\noindent Once each individual belongs to a layer, the fitness assignment is accomplished layer-by-layer.
+The initial fitness of the first layer is assigned based on the number of points in the entire population.
+The similarity of an individual to other individuals in the current layer is evaluated based on the maximum and minimum values within that layer.
+This may be done in terms of the objective or the design space.
+For this project, similarity was computed in the objective space.
+Finally, based on the similarity of each individuals, a niche count is assigned to that individual and the final shared fitness of that individual is assigned by the ratio of the initial layer fitness and the individual niche count.
+The next layer is then evaluated in the same manner with its initial fitness based on the minimum shared fitness value of the previous layer.
+\newline
+
+\noindent Within NSGA, there are certain parameters which affect the final generation of the Pareto frontier.
+It was found for the test problems, the selection of the fitness degradation parameter, $\epsilon$, and the sharing parameter, $\sigma$, were the most important.
+The fitness degradation parameter, $\epsilon$, affects the difference in initial fitness values between layers.
+The larger the value of $\epsilon$, the higher a penalty is placed on individuals in non-dominated layers that are not in the Pareto layer.
+The sharing parameter, $\sigma$, affects the closeness of the final Pareto points.
+The higher the value of $\sigma$, the more "gaps" in the frontier.
+\newline
+
+\noindent The next sections shall discuss the unconstrained problems ZDT1, ZDT2, and ZDT3, the results from the fitness function NSGA and MATLAB's "ga" function as well as the results from MATLAB's "gamultiobj" function for each.
 
 \subsection{ZDT1} 
-The first test problem, denoted as ZDT1 in (insert reference) is shown below.
+The first test problem, denoted as ZDT1 in \cite{deb2001multi} is shown below.
 
@@
 
-The true Pareto frontier for this problem occurs when $x_i = 0$ for i = 2,...,30.
+\noindent The true Pareto frontier for this problem occurs when $x_i = 0$ for i = 2,...,30.
 Figure~\ref{fig:ZDT1} shows a sample result from both MATLABs built in MOGA and the MOGA developed in this project.
@@
 \end{table}
-From these metrics, there is certainly a trade-off between MATLABs MOGA and the MOGA developed in this project.
+\begin{figure}[h]
+  \caption{ZDT1 Quality Metrics}
+  \centering
+  \includegraphics[width=0.85\textwidth]{ZDT1_QM.png}  
+  \label{fig:ZDT1_QM}
+\end{figure}
+
+\noindent From these metrics, there is certainly a trade-off between MATLABs MOGA and the MOGA developed in this project.
 The coverage difference of the new MOGA is better in this problem whereas the Pareto spread is improved when using MATLABs MOGA.
@@
 \subsection{ZDT2} 
-The second test problem, denoted as ZDT2 in (insert reference) is shown below.
+The second test problem, denoted as ZDT2 in \cite{deb2001multi} is shown below.
 
@@
 
-The true Pareto frontier for this problem, similar to ZDT1, occurs when $x_i$ = 0 for i = 2,...,30.
+\noindent The true Pareto frontier for this problem, similar to ZDT1, occurs when $x_i$ = 0 for i = 2,...,30.
 Figure~\ref{fig:ZDT2} shows a sample result from both MATLABs built in MOGA and the MOGA developed in this project.
@@
 \end{table}
+\begin{figure}[h]
+  \caption{ZDT2 Quality Metrics}
+  \centering
+  \includegraphics[width=0.85\textwidth]{ZDT2_QM.png}  
+  \label{fig:ZDT2_QM}
+\end{figure}
 
 \subsection{ZDT3} 
-The third test problem, denoted as ZDT3 in (insert reference) is shown below.
+The third test problem, denoted as ZDT3 in \cite{deb2001multi} is shown below.
 
@@
 
-The true Pareto frontier for this problem again occurs when $x_i$ = 0 for i = 2,...,30.
+\noindent The true Pareto frontier for this problem again occurs when $x_i$ = 0 for i = 2,...,30.
 Figure~\ref{fig:ZDT3} shows a sample result from both MATLABs built in MOGA and the MOGA developed in this project.
 Table~\ref{tab:ZDT3} summarizes the mean quality metrics for each algorithm for ten runs.
+\newline
 
@@
 \end{table}
+\begin{figure}[h]
+  \caption{ZDT3 Quality Metrics}
+  \centering
+  \includegraphics[width=0.85\textwidth]{ZDT3_QM.png}  
+  \label{fig:ZDT3_QM}
+\end{figure}
 
-Overall, MATLABs MOGA outperforms the MOGA developed in this project in both coverage difference and Pareto spread.
+\noindent Overall, MATLABs MOGA outperforms the MOGA developed in this project in both coverage difference and Pareto spread.
 A paired t-test shows that the difference in the means for coverage difference is statistically significant (p<0.05), while the difference is not statistically significant in Pareto Spread (p=0.21).
+\newline
+
+\noindent Overall, our MOGA outperformed MATLABs MOGA in both quality metrics.
+However, by examining the Pareto frontiers, it is clear that neither algorithm is truely satisfactory in estimating the true Pareto frontier.
+
+\section{Constrained MOGA Problems}
+
+There are many ways in which fitness evaluation can be accomplished for constraints.
+In general, some factors which should be included in fitness evaluation are the feasibility of an individual, the amount of infeasibility, and the number of violated constraints for a certain individual.
+Several methods to take into account these factors are described in \cite{kurpati2002constraint}.
+For this project, all three parameters are used to evaluated the fitness of individuals in constrained problems.
+This method is denoted at CH-I4 in \cite{kurpati2002constraint}.
+\newline
+
+\noindent As in the unconstrained algorithm, there are fitness parameters which can be chosen to place more or less emphasis on any of the factors (i.e., amount of feasibility, etc.).
+For each test problem, these factors were chosen such that the "best" resulting Pareto frontier could be obtained.
+"Best", here is meant to describe the Pareto spread and coverage difference of the resulting frontier.
+The two factors which could be tuned in this algorithm were denoted as CF1 and CF2.
+CF1 is the factor affects the emphasis on the amount of infeasibility of an individual.
+Whereas CF2 affects the emphasis on the number of violated constraints.
+\newline
+
+\noindent The following sections shall discuss the test problems OSY, TNK, and CTP, the results from the constrained fitness function with MATLAB's "ga" function and from MATLAB's "gamultiobj".
 
 \subsection{OSY} 
-This test problem, denoted as OSY in (insert reference) is shown below, Figure~\ref{fig:OSY_true} shows the true Pareto frontier for this problem.
+This test problem, denoted as OSY in \cite{deb2001multi} is shown below, Figure~\ref{fig:OSY_true} shows the true Pareto frontier for this problem.
 
@@
 
-Figure~\ref{fig:OSY} shows a sample result from both MATLABs built in MOGA and the MOGA developed in this project.
+\noindent Figure~\ref{fig:OSY} shows a sample result from both MATLABs built in MOGA and the MOGA developed in this project.
 Table~\ref{tab:OSY} summarizes the mean quality metrics for each algorithm for ten runs.
@@
 \end{table}
-
-Overall, our MOGA outperformed MATLABs MOGA in both quality metrics.
-However, by examining the Pareto frontiers, it is clear that neither algorithm is truely satisfactory in estimating the true Pareto frontier.
-
-\section{Constrained MOGA Problems}
-This is a reference to Azarms constraint paper \cite{kurpati2002constraint}. %This is how references are read from the references.bib file.
+\begin{figure}[h]
+  \caption{OSY Quality Metrics}
+  \centering
+  \includegraphics[width=0.85\textwidth]{OSY_QM.png}  
+  \label{fig:OSY_QM}
+\end{figure}
 
 \subsection{TNK} 
-This test problem, denoted as TNK in (insert reference) is shown below with the true Pareto frontier shown in Figure~\ref{fig:TNK_true}.
+This test problem, denoted as TNK in \cite{deb2001multi} is shown below with the true Pareto frontier shown in Figure~\ref{fig:TNK_true}.
 
@@
 
-Figure~\ref{fig:TNK} shows a sample result from both MATLABs built in MOGA and the MOGA developed in this project.
+\noindent Figure~\ref{fig:TNK} shows a sample result from both MATLABs built in MOGA and the MOGA developed in this project.
 Table~\ref{tab:TNK} summarizes the mean quality metrics for each algorithm for ten runs.
@@
 \end{table}
+\begin{figure}[h]
+  \caption{TNK Quality Metrics}
+  \centering
+  \includegraphics[width=0.85\textwidth]{TNK_QM.png}  
+  \label{fig:TNK_QM}
+\end{figure}
 
-Comparing the estimated Pareto frontiers to the true Pareto frontier, is is clear that our MOGA outperforms MATLAB's MOGA.
+\noindent Comparing the estimated Pareto frontiers to the true Pareto frontier, is is clear that our MOGA outperforms MATLAB's MOGA.
 The Pareto spread in our MOGA is significantly higher however the coverage difference is higher in MATLABs MOGA (p<0.05).
@@
 \subsection{CTP} 
-This test problem, denoted as CTP in (insert reference) is shown below and the true Pareto frontier is shown in Figure~\ref{fig:CTP_true}.
+This test problem, denoted as CTP in \cite{deb2001multi} is shown below and the true Pareto frontier is shown in Figure~\ref{fig:CTP_true}.
 
@@
 
-Figure~\ref{fig:CTP} shows a sample result from both MATLABs built in MOGA and the MOGA developed in this project.
+\noindent Figure~\ref{fig:CTP} shows a sample result from both MATLABs built in MOGA and the MOGA developed in this project.
 Table~\ref{tab:CTP} summarizes the mean quality metrics for each algorithm for ten runs \cite{deb2001multi}.
@@
 \end{table} 
+\begin{figure}[h]
+  \caption{CTP Quality Metrics}
+  \centering
+  \includegraphics[width=0.85\textwidth]{CTP_QM.png}  
+  \label{fig:CTP_QM}
+\end{figure}
 
-The mean values for coverage difference are exactly the same for both algorithms.
+\noindent The mean values for coverage difference are exactly the same for both algorithms.
 In fact a paired t-test also shows the means are not statistically difference(p>0.05).
@@
 \section{Robust Problems} 
+Some discussion of the robust methods here.
 
 \subsection{Robust TNK} 
-This test problem, denoted as TNK in (insert reference) is shown below with the true Pareto frontier shown in Figure~\ref{fig:TNK_true}.
+This test problem, denoted as TNK in \cite{deb2001multi} is shown below with the true Pareto frontier shown in Figure~\ref{fig:TNK_true}.
 
@@
 
-Figure~\ref{fig:robust} shows a sample result from both MATLABs built in MOGA and the robust MOGA developed in this project.
+\noindent Figure~\ref{fig:robust} shows a sample result from both MATLABs built in MOGA and the robust MOGA developed in this project.
 Table~\ref{tab:robustTNK} summarizes the mean quality metrics for each algorithm for ten runs.
@@
 \begin{table}[h]
-\caption{Quality Metrics for TNK} 
+\caption{Quality Metrics for Robust TNK (10 Runs)} 
 \centering 
@@
 \hline\hline  
-Metric & MATLABs MOGA & Our MOGA \\ \hline
-CD &  0.8581 (0.0480) & 0.7792 (0.0036) \\ \hline
-OS & 0.4177 (0.3216) & 0.9763 (0.0178)\\ \hline
+Metric &  Our MOGA \\ \hline
+CD & 0.95 (0.014) \\ \hline
+OS & 0.66 (0.012) \\ \hline
 \end{tabular}
@@
 
-Comparing the estimated Pareto frontiers to the true Pareto frontier, is is clear that our MOGA outperforms MATLAB's MOGA.
+\noindent Comparing the estimated Pareto frontiers to the true Pareto frontier, is is clear that our MOGA outperforms MATLAB's MOGA.
 The Pareto spread in our MOGA is significantly higher however the coverage difference is higher in MATLABs MOGA (p<0.05).
@@
 \end{align*}
-	The function $flightTime(\textbf{x},\textbf{y})$ is a black-box.
+
+\noindent The function $flightTime(\textbf{x},\textbf{y})$ is a black-box.
 The values $\textbf{xc}_j$ and  $\textbf{yc}_j$ specify the exclusion zone centers while $\textbf{r}_j$ specify the radii.
@@
 
-\section{Appendix}
-
-%Matlab codes starts here
-
-\lstset{language=Matlab,%
-    %basicstyle=\color{red},
-    breaklines=true,%
-    morekeywords={matlab2tikz},
-    keywordstyle=\color{blue},%
-    morekeywords=[2]{1}, keywordstyle=[2]{\color{black}},
-    identifierstyle=\color{black},%
-    stringstyle=\color{mylilas},
-    commentstyle=\color{mygreen},%
-    showstringspaces=false,%without this there will be a symbol in the places where there is a space
-    numbers=left,%
-    numberstyle={\tiny \color{black}},% size of the numbers
-    numbersep=8pt, % this defines how far the numbers are from the text
-    emph=[1]{for,end,break},emphstyle=[1]\color{red}, %some words to emphasise
-    %emph=[2]{word1,word2}, emphstyle=[2]{style},    
-}
-
-\section*{Matlab Code}
-
-\lstinputlisting{MasterCode.m}
-\lstinputlisting{fitFCN5.m}
-
 \end{document}

### 2017-05-05 ENME625_parta.m
still not getting the results I want

@@ -1,5 +1,5 @@
 clear all; close all; clc; warning off;
-rng(4)
+
 global alpha sigma epsilon Mmoga CF1 CF2
 
 prompt2 = 'Run full code or see results only? \n 1 - Run Full Code \n 2 - Results only \n';

### 2017-05-05 fitFCN5.m

@@ -96,6 +96,7 @@ else
      
     infeas_pop = func(infeasible_indecies,:);
     feas_pop = func(feasible_indecies,:);
+    fit_constr = 0;
     % Evaluate rank for infeasible individuals
     if ~isempty(infeas_pop)
         %g = infeas_pop(:,nfunc+1:nconstr+nfunc);
@@ -157,13 +158,17 @@ else
           dominant_feasible = zeros(M,1);
           dominant_feasible(feasible_indecies) = place;
           %rank(place == 1) = 1;
-          if sum(place) > 500000          
+          if sum(feasible_indecies) > 1          
               fit = -NSGA(feas_pop(:,1:nfunc));
-              %fit = (1-fit/max(fit))+min(rank);
-              %rank(feasible_indecies) = fit;
+              %scaled_fit = -(1-fit/max(fit))+max(fit_constr);
+              scaled_fit = fit;
+              rank(feasible_indecies) = scaled_fit +100000;
           else
-              rank(dominant_feasible ==1 ) = 1;
+              rank(dominant_feasible ==1 ) = max(fit_constr)+100000;
           end
+          
+          
+          
           %m = 1;
           %for k = 1:length(place)
           %    if place(k) == 1
@@ -171,9 +176,26 @@ else
           %    end
           %end     
      end
-        
-    end
-    fit = rank;
+     
+     if(sum(rank(infeasible_indecies)>0) > 0)
+        fprintf('ah! what is happening') 
+     end
+     
+     if(sum(rank>50000000000)>0)
+         fprintf('somehow something is unnassigned')
+     end
+    
+     %if(sum(feasible_indecies)>50)
+     %    fprintf('feasible_pop')
+     %end
+    fit = -rank;
+    
+    figure(5)
+    scatter(func(:,1),func(:,2),5*ones(length(func),1),rank)
+    axis([0,3,0,3])
+
+    colorbar
+    pause(0.01)
 
 
 end

### 2017-05-06 FlightPathOpt.m
fixing metrics for FPP

@@ -152,6 +152,7 @@ else
     options = optimoptions(options,'Display', 'final');
     %options = optimoptions(options,'PlotFcn', { @gaplotpareto });
     options = optimoptions(options,'ParetoFraction', 0.9);
+    options = optimoptions(options,'PopulationSize', 300);
     [X,FVAL,EXITFLAG,OUTPUT,POPULATION,SCORE] = gamultiobj(problem_function,length(ic),[],[],[],[],lb,ub,problem_constraints,options);
 end
 

### 2017-05-06 coverageDifference2.m

@@ -6,15 +6,8 @@ function val = coverageDifference2(input)
 % [ f1_n ,f2_n]
 min_f1 = min(input(:,1)); max_f1 = max(input(:,1));
 min_f2 = min(input(:,2)); max_f2 = max(input(:,2));
-if min_f1<0
-    input(:,1) = input(:,1)+abs(min_f1);
-end
-if min_f2<0
-    input(:,2) = input(:,2)+abs(min_f2);
-end
-%normalize range
-input(:,1) = input(:,1)./(max_f1-abs(min_f1));
-input(:,2) = input(:,2)./(max_f2-abs(min_f2));
+input(:,1) = (input(:,1)-min_f1)/(max_f1 -min_f1);
+input(:,2) = (input(:,2)-min_f2)/(max_f2 - min_f2);
 
 vals = 1-input;
 

### 2017-05-06 flightConstraints.m

@@ -1,3 +1,12 @@
 function [ineq, eq] = flightConstraints(PathPoints,sizeX,sizeY,xc,yc,radius)
 ineq =  radius' - getDistanceExclustionZone(PathPoints,sizeX,sizeY,xc,yc,radius);
 eq = 0;
+pts = reshape(PathPoints,2,[])';
+dist_constraint = zeros(length(pts),1);
+for i = 1:length(dist_constraint)
+    other_indecies = ones(length(dist_constraint),1); other_indecies(i) = 0;
+    other_pts = pts(other_indecies ==1,:);
+    dist_constraint(i) = 1 - min(sqrt( (pts(i,1) - other_pts(:,1)).^2 + (pts(i,2)-other_pts(:,2)).^2));
+end
+ineq = [ineq;dist_constraint];
+

### 2017-05-06 getMetricsFPP.m

@@ -1,0 +1,36 @@
+%Get Metrics:
+function [CD,spread,fval] = getMetricsFPP(fval)
+if nargin == 0 
+    n=1; i =1;
+    fval = cell(10,1);
+    
+    while n < 11
+        
+        f = FlightPathOpt(i+15);
+        i=i+1;
+        if length(f)==90
+            CD = coverageDifference2(f);
+            if( CD < 100)
+                fval{n,1} =f;
+                n=n+1;
+            end
+        end
+    end    
+end
+
+
+CD = zeros(10,1);
+all_points = [];
+for i = 1:10
+    CD(i) = coverageDifference2(fval{i,1});
+    all_points = [all_points ; fval{i,1}];
+end
+
+spread = zeros(10,1);
+ideal = min(all_points);
+nadir = max(all_points);
+for i =1:10
+    spread(i) = ParetoSpread(fval{i,1},nadir,ideal);
+end
+
+

### 2017-05-06 draft1_SM.tex
added more content

@@
 \definecolor{mylilas}{RGB}{170,55,241}
+\usepackage{float}
+\floatplacement{figure}{H}
+
+\usepackage{caption}
 
@@
 \noindent The next sections shall discuss the unconstrained problems ZDT1, ZDT2, and ZDT3, the results from the fitness function NSGA and MATLAB's "ga" function as well as the results from MATLAB's "gamultiobj" function for each.
-
+\newpage
 \subsection{ZDT1} 
@@
 Ten runs for each algorithm were performed and the mean and standard deviation of each metric are tabulated in Table~\ref{tab:ZDT1}.
+
 \begin{figure}[h]
@@
 
+\newpage
 \subsection{ZDT2} 
@@
 Table~\ref{tab:ZDT2} summarizes the mean quality metrics for each algorithm for ten runs.
-\begin{figure}[h!]
+\begin{figure}[H]
   \caption{Example Pareto Results for ZDT2}
@@
 
-\begin{table}[h]
+\begin{table}[H]
 \caption{Quality Metrics for ZDT2} 
@@
 \end{table}
-\begin{figure}[h]
+\begin{figure}[H]
   \caption{ZDT2 Quality Metrics}
@@
 \end{figure}
+\newpage
+\newpage
+\newpage
+\goodbreak
+\newpage
 
+\goodbreak
+
+\newpage
+\goodbreak
 \subsection{ZDT3} 
@@
 
-\begin{figure}[h]
+\begin{figure}[H]
   \caption{Example Pareto Results for ZDT3}
@@
 
-\begin{table}[h]
+\begin{table}[H]
 \caption{Quality Metrics for ZDT3} 
@@
 \end{align*}
-\begin{figure}[h]
+\begin{figure}[H]
   \caption{True Pareto Frontier for OSY}
@@
 
-\begin{table}[h]
+\begin{table}[H]
 \caption{Quality Metrics for OSY} 
@@
 \end{table}
-\begin{figure}[h]
+\begin{figure}[H]
   \caption{OSY Quality Metrics}
@@
 \end{figure}
-
+\newpage
 \subsection{TNK} 
@@
 \end{align*}
-\begin{figure}[h]
+\begin{figure}[H]
   \caption{True Pareto Frontier for TNK}
@@
 
-\begin{table}[h]
+\begin{table}[H]
 \caption{Quality Metrics for TNK} 
@@
 \end{table}
-\begin{figure}[h]
+\begin{figure}[H]
   \caption{TNK Quality Metrics}
@@
 The Pareto spread in our MOGA is significantly higher however the coverage difference is higher in MATLABs MOGA (p<0.05).
-
+\newpage
 \subsection{CTP} 
@@
 \end{align*}
-\begin{figure}[h]
+\begin{figure}[H]
   \caption{True Pareto Frontier for CTP}
@@
 
-\begin{table}[h]
+\begin{table}[H]
 \caption{Quality Metrics for CTP} 
@@
 \end{table} 
-\begin{figure}[h]
+\begin{figure}[H]
   \caption{CTP Quality Metrics}
@@
 For Pareto spread, MATLAB's MOGA performs the highest.
+\newpage
+\section{Robust Problems} 
+To solve problems with an uncertain variable we implement RMOGA.
+One way to ensure robustness for a given population considered in GA, is by finding the value of the uncertain variable which maximizes the constraint values acording to each member in the population.
+Another way is to discretize the dependent variable and then find which uncertain variable in this set maximizes the constraint values.
+This latter method is the one we chose because of the decreased execution time over the former.
+These two options are shown in figure \ref{fig:discretize}.
+   Since the uncertainty term only appears in the constraints portion of both of the problems we consider this discretization is fairly simple.
+In addition, since the uncertain terms are linearly combined in the constraints, this discretization is trivial.
 
-\section{Robust Problems} 
-Some discussion of the robust methods here.
+\begin{figure}[H]
+  \caption{Options for making optimization robust to uncertain variables. }
+  \centering
+  \includegraphics[width=0.85\textwidth]{Robustness.png}  
+  \label{fig:discretize}
+\end{figure}
 
@@
 Table~\ref{tab:robustTNK} summarizes the mean quality metrics for each algorithm for ten runs.
-\begin{figure}[h]
+\begin{figure}[H]
   \caption{Example Pareto Results for TNK}
@@
 
-\begin{table}[h]
+\begin{table}[H]
 \caption{Quality Metrics for Robust TNK (10 Runs)} 
@@
 In this figure there are two exclusion zones.
-\begin{figure}[h]
+\begin{figure}[H]
   \caption{True Pareto Frontier for CTP}
@@
 
-\begin{figure}[h]
+\begin{figure}[H]
   \caption{True Pareto Frontier for CTP}
@@
 
- \newpage
+\begin{table}[H]
+\caption{Quality Metrics for Robust FPP (10 Runs)} 
+\centering 
+\begin{tabular}{|c|c|c|} 
+\hline\hline  
+Metric &  Our MOGA \\ \hline
+CD & 0.2427 (0.0704) \\ \hline
+OS & 0.4794 (0.1220) \\ \hline
+\end{tabular}
+\label{tab:robustTNK} 
+\end{table}
+
+%
+%\begin{table}[h]
+%\caption{Quality Metrics for Robust FPP with waypoint constraints(10 Runs)} 
+%\centering 
+%\begin{tabular}{|c|c|c|} 
+%\hline\hline  
+%Metric &  Our MOGA \\ \hline
+%CD & 0.27 0.0269) \\ \hline
+%OS & 0.4794 (0.1220) \\ \hline
+%\end{tabular}
+%\label{tab:robustTNK} 
+%\end{table}
+
 \vspace{-0.1in}

### 2017-05-06 flightConstraints.m

@@ -1,12 +1,14 @@
 function [ineq, eq] = flightConstraints(PathPoints,sizeX,sizeY,xc,yc,radius)
 ineq =  radius' - getDistanceExclustionZone(PathPoints,sizeX,sizeY,xc,yc,radius);
 eq = 0;
-pts = reshape(PathPoints,2,[])';
-dist_constraint = zeros(length(pts),1);
-for i = 1:length(dist_constraint)
-    other_indecies = ones(length(dist_constraint),1); other_indecies(i) = 0;
-    other_pts = pts(other_indecies ==1,:);
-    dist_constraint(i) = 1 - min(sqrt( (pts(i,1) - other_pts(:,1)).^2 + (pts(i,2)-other_pts(:,2)).^2));
-end
-ineq = [ineq;dist_constraint];
+
+% Using con
+%pts = reshape(PathPoints,2,[])';
+%dist_constraint = zeros(length(pts),1);
+%for i = 1:length(dist_constraint)
+%    other_indecies = ones(length(dist_constraint),1); other_indecies(i) = 0;
+%    other_pts = pts(other_indecies ==1,:);
+%    dist_constraint(i) = 1 - min(sqrt( (pts(i,1) - other_pts(:,1)).^2 + (pts(i,2)-other_pts(:,2)).^2));
+%end
+%ineq = [ineq;dist_constraint];
 

### 2017-05-06 getMetricsFPP.m

@@ -8,7 +8,7 @@ if nargin == 0
         
         f = FlightPathOpt(i+15);
         i=i+1;
-        if length(f)==90
+        if length(f)>90
             CD = coverageDifference2(f);
             if( CD < 100)
                 fval{n,1} =f;

### 2017-05-09 draft1_SM.tex
Update draft1_SM.tex

@@
 The last case was developed such that uncertainty in function parameters could be handled and robustly optimized against.
+\newline
 
@@
 The higher the value of $\sigma$, the more "gaps" in the frontier.
+For each problem, these parameters were randomly tuned such that the "best" Pareto frontier (in terms of coverage difference and Pareto spread).
 \newline
@@
 Figure~\ref{fig:ZDT1} shows a sample result from both MATLABs built in MOGA and the MOGA developed in this project.
-The quality metrics chosen to evaluate this problem are Coverage Difference (CD)and Pareto Spread (OS).
-Ten runs for each algorithm were performed and the mean and standard deviation of each metric are tabulated in Table~\ref{tab:ZDT1}.
+In this problem, $\alpha=1$, $\sigma = 0.158$, and $\epsilon = 0.22$.
+The final results were found using 300 chromosomes in each population.
+The quality metrics chosen to evaluate this problem (and all other problems) are Coverage Difference (CD) and Pareto Spread (OS).
+Ten runs for each algorithm were performed using the same initialization parameters and the mean and standard deviation of each metric are tabulated in Table~\ref{tab:ZDT1}.
 
@@
 \noindent From these metrics, there is certainly a trade-off between MATLABs MOGA and the MOGA developed in this project.
-The coverage difference of the new MOGA is better in this problem whereas the Pareto spread is improved when using MATLABs MOGA.
+The coverage difference of the new MOGA is lower (and therefore superior) in this problem whereas the Pareto spread is improved when using MATLABs MOGA.
 
@@
 \noindent The true Pareto frontier for this problem, similar to ZDT1, occurs when $x_i$ = 0 for i = 2,...,30.
+Selected parameters were similar to ZDT1 where $\alpha = 0.5$, $\sigma=0.5$, $\epsilon=0.22$; the number of chromosomes was 300.
 Figure~\ref{fig:ZDT2} shows a sample result from both MATLABs built in MOGA and the MOGA developed in this project.
-Table~\ref{tab:ZDT2} summarizes the mean quality metrics for each algorithm for ten runs.
+Table~\ref{tab:ZDT2} summarizes the mean quality metrics for each algorithm over ten runs.
 \begin{figure}[H]
@@
 \noindent The true Pareto frontier for this problem again occurs when $x_i$ = 0 for i = 2,...,30.
+The fitness parameters selected in this problem were $\alpa = 1$, $\sigma = 0158$ and $\epsilon = 0.22$.
+Again, the number of chromosomes in this problem was 300.
 Figure~\ref{fig:ZDT3} shows a sample result from both MATLABs built in MOGA and the MOGA developed in this project.
@@
 
-\noindent Overall, our MOGA outperformed MATLABs MOGA in both quality metrics.
-However, by examining the Pareto frontiers, it is clear that neither algorithm is truely satisfactory in estimating the true Pareto frontier.
-
 \section{Constrained MOGA Problems}
 
-There are many ways in which fitness evaluation can be accomplished for constraints.
-In general, some factors which should be included in fitness evaluation are the feasibility of an individual, the amount of infeasibility, and the number of violated constraints for a certain individual.
+There are many ways in which fitness evaluation can be accomplished for constrainted problems.
+In general, some factors which may be included in fitness evaluation are the feasibility of an individual, the amount of infeasibility, and the number of violated constraints for a certain individual.
 Several methods to take into account these factors are described in \cite{kurpati2002constraint}.
@@
 This test problem, denoted as OSY in \cite{deb2001multi} is shown below, Figure~\ref{fig:OSY_true} shows the true Pareto frontier for this problem.
+The factors chosen for this problem were $CF1 = 0.005$ and $CF2 = 0.015$, this placed a higher weight of the number of constraint violations than the amount of infeasibility.
 
@@
 This test problem, denoted as TNK in \cite{deb2001multi} is shown below with the true Pareto frontier shown in Figure~\ref{fig:TNK_true}.
+Constraint parameters CF1 and CF2 were both chosen to be 0.01 to place equal emphasis on amount of infeasibility and number of violated constraints.
 
@@
 This test problem, denoted as CTP in \cite{deb2001multi} is shown below and the true Pareto frontier is shown in Figure~\ref{fig:CTP_true}.
+Just as in TNK, constraint parameters CF1 and CF2 were both chosen to be 0.01 to place equal emphasis on amount of infeasibility and number of violated constraints.
 
@@
 Table~\ref{tab:robustTNK} summarizes the mean quality metrics for each algorithm for ten runs.
+\newline
 \begin{figure}[H]
@@
 
+\section{Conclusion}
+
+Overall, it was found that different optimization algorithms result in a range of solutions for a given test problem.
+Thus it is important, when developing an optimization algorithm, to test against a range of optimization problems.
+In addition, it was also concluded that special attention should be paid to tunable parameters within each algorithm.
+Understanding the nature of the parameter and how it affects the algorithm is crucial to obtaining the "true" Pareto frontier.
+
 \vspace{-0.1in}

### 2017-05-10 draft1_SM.tex
merging changes
added more content

@@
 A fitness function for the first two cases was developed using the built-in MATLAB 'ga' routine.
-The last case was developed such that uncertainty in function parameters could be handled and robustly optimized against.
-\newline
+The last case was developed such that uncertainty in function parameters could be handled and robustly optimized against.\newline
 
-\noindent Each method developed was evaluated through the use of well-known test problems.
+\noindent For the first two methods, each method developed was evaluated through the use of well-known test problems.
 The resulting Pareto frontier of each method was evaulated in terms of quality metrics.
-Finally, the results of the developed methods were compared to results obtained by using the built-in MATLAB 'gamultiobj' routine.
+Finally, the results of the developed methods were compared to results obtained by using the built-in MATLAB 'gamultiobj' routine for the unconstrained and constrained cases.
+In the first robust problem, we compare the results against the non-robust MOGA.
+In the second robust problem there is not an objective comparison.
 
@@
 The final results were found using 300 chromosomes in each population.
-The quality metrics chosen to evaluate this problem (and all other problems) are Coverage Difference (CD) and Pareto Spread (OS).
+The quality metrics chosen to evaluate this problem (and all other problems) are Coverage Difference (CD) and Overall Pareto Spread (OS).
 Ten runs for each algorithm were performed using the same initialization parameters and the mean and standard deviation of each metric are tabulated in Table~\ref{tab:ZDT1}.
 
-\begin{figure}[h]
+\begin{figure}[H]
   \caption{Example Pareto Results for ZDT1}
@@
 
-\begin{table}[h]
+\begin{table}[H]
 \caption{Quality Metrics for ZDT1} 
@@
 \end{table}
-\begin{figure}[h]
+\begin{figure}[H]
   \caption{ZDT1 Quality Metrics}
@@
 \begin{tabular}{|c|c|c|} 
-\hline\hline  
+\hline 
 Metric & MATLABs MOGA & Our MOGA \\ \hline
@@
 \end{figure}
-\newpage
-\newpage
-\newpage
-\goodbreak
+
 \newpage
 
-\goodbreak
-
-\newpage
-\goodbreak
 \subsection{ZDT3} 
@@
 \noindent The true Pareto frontier for this problem again occurs when $x_i$ = 0 for i = 2,...,30.
-The fitness parameters selected in this problem were $\alpa = 1$, $\sigma = 0158$ and $\epsilon = 0.22$.
+The fitness parameters selected in this problem were $\alpha = 1$, $\sigma = 0158$ and $\epsilon = 0.22$.
 Again, the number of chromosomes in this problem was 300.
@@
 \end{table}
-\begin{figure}[h]
+\begin{figure}[H]
   \caption{ZDT3 Quality Metrics}
@@
 Table~\ref{tab:OSY} summarizes the mean quality metrics for each algorithm for ten runs.
-\begin{figure}[h]
+\begin{figure}[H]
   \caption{Example Pareto Results for OSY}
@@
 \begin{tabular}{|c|c|c|} 
-\hline\hline  
+\hline
 Metric & MATLABs MOGA & Our MOGA \\ \hline
@@
 Table~\ref{tab:TNK} summarizes the mean quality metrics for each algorithm for ten runs.
-\begin{figure}[h]
+\begin{figure}[H]
   \caption{Example Pareto Results for TNK}
@@
 Table~\ref{tab:CTP} summarizes the mean quality metrics for each algorithm for ten runs \cite{deb2001multi}.
-\begin{figure}[h]
+\begin{figure}[H]
   \caption{Example Pareto Results for CTP}
@@
 \begin{tabular}{|c|c|c|} 
-\hline\hline  
+\hline  
 Metric & MATLABs MOGA & Our MOGA \\ \hline
@@
 To solve problems with an uncertain variable we implement RMOGA.
-One way to ensure robustness for a given population considered in GA, is by finding the value of the uncertain variable which maximizes the constraint values acording to each member in the population.
+There are different approaches for implementing robust constraints in MOGA \cite{hu2009improving}\cite{li2006new}.
+One way to ensure robustness for a given population considered in GA, is by finding the value of the uncertain variable which maximizes the constraint values according to each member in the population .
 Another way is to discretize the dependent variable and then find which uncertain variable in this set maximizes the constraint values.
@@
    Since the uncertainty term only appears in the constraints portion of both of the problems we consider this discretization is fairly simple.
-In addition, since the uncertain terms are linearly combined in the constraints, this discretization is trivial.
+In addition, since the uncertain terms are linearly combined in the constraints.
 
@@
 
-\noindent Figure~\ref{fig:robust} shows a sample result from both MATLABs built in MOGA and the robust MOGA developed in this project.
+\noindent Figure~\ref{fig:robustTNK} shows a sample result from both MATLABs built in MOGA and the robust MOGA developed in this project.
 Table~\ref{tab:robustTNK} summarizes the mean quality metrics for each algorithm for ten runs.
@@
 \begin{tabular}{|c|c|c|} 
-\hline\hline  
+\hline 
 Metric &  Our MOGA \\ \hline
@@
 \noindent Comparing the estimated Pareto frontiers to the true Pareto frontier, is is clear that our MOGA outperforms MATLAB's MOGA.
-The Pareto spread in our MOGA is significantly higher however the coverage difference is higher in MATLABs MOGA (p<0.05).
+The Pareto spread in our MOGA is significantly higher however the coverage difference is higher in MATLABs MOGA ($p<0.05$ ).
 
@@
 Now let us consider the final problem where we try to minimize the total flight time from the start location $(0,12.5)$ to the finish location $(40,12.5)$.
-In this problem there is a know wind velocity field which changes the total velocity of the aircraft with respect to the ground.
-At the same time, we want to maximize the distance of the flight path from some group of some exclusion zones.
+In this problem there is a known wind velocity field which changes the total velocity of the aircraft with respect to the ground.
+At the same time, we want to maximize the distance of the flight path from the centers of a group of exclusion zones.
 This also introduces a constraint that requires the flight path not intersect the exclusion zone.
@@
 A solution to this problem is shown in figure \ref{fig:FPP}.
-In this figure there are two exclusion zones.
+In this figure there are two exclusion zones marked in blue.
+Since this is a bi-objective function, there are multiple optimal solutions.
+These solutions are form a Pareto Frontier.
+The distances to the closest exclusion zone center are negative because this is a maximization problem.
 \begin{figure}[H]
-  \caption{True Pareto Frontier for CTP}
+  \caption{Flight Path with exclusion zones. The exclusion zones are marked in blue.  The dotted blue line indicates the robust boundary.}
   \centering
@@
   \centering
-  \includegraphics[width=0.85\textwidth]{FPP_pareto.png}  
+  \includegraphics[width=0.85\textwidth]{FPP_pareto_units.png}  
   \label{fig:FPP_pareto}
@@
 \begin{tabular}{|c|c|c|} 
-\hline\hline  
+\hline  
 Metric &  Our MOGA \\ \hline
@@
 \end{tabular}
-\label{tab:robustTNK} 
+\label{tab:robustFPP} 
 \end{table}
+
+We chose to approach the robust FPP using a constraint which maximizes the distance of the \bf closest \rm point in the trajectory to the exclusion zone.
+If we try to maximize the distance of all of the points, then the optimization will take advantage of the way that the flight path is approximated by the waypoints;  all of the waypoints will be stacked in the corner farthest from the exclusion zone and there is a risk that the fitted path will pass through the exclusion zone.
+Maximizing the closest point side-steps this problem.
+
+Another interesting thing about this problem is when there are two exclusion zones, it is easy to see that the Pareto frontier maximizing  the distance approaches the midpoint between the two exclusion zones.
+This phenomena is visible in figure \ref{fig:FPP_pareto} where the midpoint is at $12.5$ m from the exclusion zone and the Pareto Frontier approaches it.
 
@@
 Understanding the nature of the parameter and how it affects the algorithm is crucial to obtaining the "true" Pareto frontier.
+In addition, we were impressed with GA's ability to find many different minima; the presence of multiple minima would be a problem for a gradient based solver.
+Of course the increased time to a solution with no guarantee of optimality is the trade-off when using sampling algorithm.
 

### 2017-05-11 ENME625_parta.m
Add files via upload

@@ -1,5 +1,5 @@
 clear all; close all; clc; warning off;
-
+tic
 global alpha sigma epsilon Mmoga CF1 CF2 DP
 prompt3 = 'Would you like to run Test Problems or Flight Path Problem? \n 1 - Test Problems \n 2 - Flight Path Problem';
 FPPYN = input(prompt3);
@@ -10,6 +10,11 @@ if FPPYN == 1
 
     prompt = 'Which Test Problem Do You Want To Run? \n 1 - ZDT1\n 2 - ZDT2 \n 3 - ZDT3 \n 4 - OSY \n 5 - TNK \n 6 - CTP \n 7 - TNK Robust';
     prob = input(prompt);
+    
+    if runType == 2
+        prompt4 = 'There are 10 example test runs for this problem. Which one would you like to see? (1-10)';
+        testnum = input(prompt4);
+    end
 
     %% Load Selected Problem and Optimization Parameters
 
@@ -85,8 +90,17 @@ if FPPYN == 1
         plot(Pareto(:,1),Pareto(:,2),'gv','LineWidth',2,'MarkerSize',10)
         hold on; grid on; legend('MATLABs MOGA','Our MOGA')
         xlabel('f_1'); ylabel('f_2')
+        
+        CD = coverageDifference2(Pareto); %Coverage Difference of Our MOGA
+        CD_M = coverageDifference2(Fmoga(:,1:2));  %Coverage Difference of MATLABs MOGA
+
+        max_P1 = max(true_P(:,1)); min_P1 = min(true_P(:,1));
+        max_P2 = max(true_P(:,2)); min_P2 = min(true_P(:,2));
+
+        OS = ParetoSpread(Pareto,[max_P1 max_P2],[min_P1 min_P2]); %Pareto Spread of Our MOGA
+        OS_M = ParetoSpread(Fmoga,[max_P1 max_P2],[min_P1 min_P2]); %Pareto Spread of MATLABs MOGA
     elseif runType == 2
-        test = 1;
+        test = testnum;
         load(['results_and_params',num2str(prob),'_nChr',num2str(nChrome),'_nRun',num2str(nRun),'_nTest',num2str(test)])
         close;
 
@@ -107,10 +121,10 @@ if FPPYN == 1
         OS_M = ParetoSpread(Fmoga,[max_P1 max_P2],[min_P1 min_P2]); %Pareto Spread of MATLABs MOGA
 
     end
[…]

### 2017-05-11 FuncParams.m

@@ -40,7 +40,7 @@ switch prob
         A = [-1 -1 0 0 0 0;1 1 0 0 0 0;-1 1 0 0 0 0;1 -3 0 0 0 0]; 
         b = [-2;6;2;2];
         Aeq = []; beq = [];
-        nChrome = 60; nRun = 100;
+        nChrome = 60; nRun = 1000;
         alpha=[]; sigma=[]; epsilon=[];
         true_P = [5,-275;75,-45];
         CF1 = 0.005; CF2 = 0.015;

### 2017-05-11 FuncParams.m
Add files via upload

@@ -1,6 +1,8 @@
 function [ params,A,b,Aeq,beq,LB,UB,true_P ] = FuncParams( prob )
 % Return the chosen optimization parameters given the problem number
 
+global DP
+
 switch prob
     case 1 % ZDT1
         nvar = 30; LB = zeros(1,nvar); UB = ones(1,nvar);

### 2017-05-11 ENME625_parta.m
Add files via upload

@@ -1,130 +1,117 @@
 clear all; close all; clc; warning off;
-tic
-global alpha sigma epsilon Mmoga CF1 CF2 DP
-prompt3 = 'Would you like to run Test Problems or Flight Path Problem? \n 1 - Test Problems \n 2 - Flight Path Problem';
-FPPYN = input(prompt3);
 
-if FPPYN == 1
-    prompt2 = 'Run full code or see results only? \n 1 - Run Full Code \n 2 - Results only \n';
-    runType = input(prompt2);
+global alpha sigma epsilon Mmoga CF1 CF2
 
-    prompt = 'Which Test Problem Do You Want To Run? \n 1 - ZDT1\n 2 - ZDT2 \n 3 - ZDT3 \n 4 - OSY \n 5 - TNK \n 6 - CTP \n 7 - TNK Robust';
-    prob = input(prompt);
-    
-    if runType == 2
-        prompt4 = 'There are 10 example test runs for this problem. Which one would you like to see? (1-10)';
-        testnum = input(prompt4);
-    end
+prompt2 = 'Run full code or see results only? \n 1 - Run Full Code \n 2 - Results only \n';
+runType = input(prompt2);
 
-    %% Load Selected Problem and Optimization Parameters
+prompt = 'Which Test Problem Do You Want To Run? \n 1 - ZDT1\n 2 - ZDT2 \n 3 - ZDT3 \n 4 - OSY \n 5 - TNK \n 6 - CTP \n';
+prob = input(prompt);
 
-    switch prob
-        case 1 % ZDT1
-            problem_function = @(X) ZDT1(X);
-            problem_constraints = [];
-        case 2 %ZDT2
-            problem_function = @(X) ZDT2(X);
-            problem_constraints = [];
-        case 3 %ZDT3
-            problem_function = @(X) ZDT3(X);
-            problem_constraints = [];
-        case 4 %OSY
-            problem_function = @(X) OSY(X);
-            problem_constraints = @OSYcon;
-        case 5 %TNK
-            problem_function = @(X) TNK(X);
-            problem_constraints = @TNKcon; 
-        case 6 %CTP
-            problem_function = @(X) CTP(X);
-            problem_constraints = @CTPcon; 
-        case 7 % Robust TNK
[…]
